### 2019-05-09 report/draft.tex
Add draft of the report
Describe the algorithm of the Ewald sum for Stokes potential. Still a draft.

% !TeX spellcheck = en_GB
\documentclass{article}[12pt]

\renewcommand{\baselinestretch}{1.3}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{latexsym}
\usepackage{mathrsfs}
\usepackage{amsthm}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage{color}
\usepackage{subfig}
\usepackage{float}
\usepackage{color}
\usepackage{titlesec}
\usepackage{bm}
\usepackage[colorlinks,linkcolor=blue,anchorcolor=green,citecolor=red]{hyperref}
\usepackage[T1]{fontenc}
\renewcommand{\rmdefault}{ptm}
\usepackage{charter}
\usepackage{fancyhdr}
\usepackage{amscd}

\usepackage{caption}
\usepackage{algorithm} %format of the algorithm
\usepackage{algorithmic} %format of the algorithm

\makeatletter
\@addtoreset{equation}{section}
\makeatother

\makeatletter % `@' now normal "letter"
\@addtoreset{equation}{section}
\makeatother  % `@' is restored as "non-letter"
\renewcommand\theequation{\oldstylenums{\thesection}%
	.\oldstylenums{\arabic{equation}}}

\usepackage{geometry}
\geometry{left=4cm,right=4cm,top=4cm,bottom=4cm}

\usepackage{listings}
\usepackage{setspace}

\begin{document}

\title{HPC Final Project}

\date{\today}

\maketitle

\section{Algorithm description}

\paragraph{Periodic Stokes potentials}
Given the Stokes equation, the Green's function for the velocity field for the free-space problem is given by the Oseen-Burgers tensor:
\begin{equation}
\mathbf{S}(\mathbf{x}) = \frac{\mathbf{1}}{|\mathbf{x}|} + \frac{\mathbf{x x}}{|\mathbf{x}|^3}.
\end{equation}
Now we consider a system of $N$ point sources at location $\mathbf{x}_n$ with strength $\mathbf{f}_n$, in the periodic setting, the velocity field is given as
\begin{equation}
\mathbf{u}(\mathbf{x}) = \sum_{n=1}^{N} \sum_{\mathbf{p}} \mathbf{S}(\mathbf{x - x_n + p}) \mathbf{f}_n, \label{eq:stokes_velocity_field}
\end{equation}     
where $\mathbf{p}$ form the discrete set $\{[iL_x \ jL_y \  kL_z]:(i, j, k) \in \mathbb{Z}^3\}$ and $L_x, L_y$ and $L_z$ are the periodic lengths in the three directions.

\paragraph{Ewald summation for Stokes}
Applying the idea of Ewald decomposition, the Eq.\eqref{eq:stokes_velocity_field} can be split as following:
\begin{equation}
\mathbf{u}(\mathbf{x}_m) = \sum_{n=1}^{N} \sum_{\mathbf{p}} \mathbf{A}(\xi, \mathbf{x_m - x_n + p}) \mathbf{f}_n + \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) e^{-k^2/4\xi^2}\sum_{n=1}^{N} \mathbf{f}_n e ^{-i \mathbf{k} \cdot (\mathbf{x}_m - \mathbf{x}_n)} - \mathbf{u}_{\text{self}} \label{eq:ewald_sum}
\end{equation} 
where $\mathbf{k} \in \{[2 \pi k_i / L_i]: k_i \in \mathbb{Z}, i=1,2,3\}, k = |\mathbf{k}|, V=L_x L_y L_z$ and $\xi$ is a positive constant known as the Ewald parameter. From the Eq.\eqref{eq:ewald_sum} we can see that the velocity field has been split into three parts: one sum in real space ($\mathbf{u}^R$), one sum in frequency domain ($\mathbf{u}^F$) and a self-contribution $\mathbf{u}_{\text{self}}$.

From the formulation by Hasimoto, we have
\begin{equation}
\mathbf{A}(\xi, \mathbf{x}) = 2 \left(\frac{\xi e^{-\xi^2 r^2}}{\sqrt{\pi} r^2} + \frac{\text{erfc}(\xi r)}{2 r^3}\right) (r^2 \mathbf{I} + \mathbf{x x}) - \frac{4 \xi}{\sqrt{\pi}} e^{-\xi^2 r^2} \mathbf{I}
\end{equation}
with $r = |\mathbf{X}|$ and
\begin{equation}
B(\xi, \mathbf{k}) = 8 \pi \left(1 + \frac{k^2}{4 \xi^2}\right) \frac{1}{k^4}(k^2 \mathbf{I} - \mathbf{k k})
\end{equation}
and
\begin{equation}
\mathbf{u}_{\text{self}}(\mathbf{x}_m) = \frac{4 \xi}{\sqrt{\pi}} \mathbf{f}_m
\end{equation}

\paragraph{Nonuniform fast Fourier transform}
The nonuniform discrete Fourier transform (NuFFT) of type 1 and 2 is defined as:
\begin{equation}
F(\mathbf{k}) = \frac{1}{N} \sum_{n=1}^N f_j e^{-i \mathbf{k} \cdot \mathbf{x}_n}
\end{equation}
and
\begin{equation}
f(x_n) = \sum_{\mathbf{k}} F(\mathbf{k}) e^{i \mathbf{k} \cdot \mathbf{x}_n}
\end{equation}
They can be computed efficiently by fast Gaussian gridding and FFT, we will introduce it in the later part.

\paragraph{Fast summation method in frequency domain}
Now we focus on the frequency domain part of the summation based on NuFFT:
\begin{equation}
\mathbf{u}^F (\mathbf{x}_m) = \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) e^{-k^2/4\xi^2}\sum_{n=1}^{N} \mathbf{f}_n e ^{-i \mathbf{k} \cdot (\mathbf{x}_m - \mathbf{x}_n)}
\end{equation}
The formula can be split into 
\begin{equation}
\mathbf{u}^F (\mathbf{x}_m) = \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) e^{-k^2/4\xi^2} \left(\sum_{n=1}^{N} \mathbf{f}_n e ^{i \mathbf{k} \cdot \mathbf{x}_n} \right)e ^{-i \mathbf{k} \cdot \mathbf{x}_m}
\end{equation}
which is one NuFFT (type 1) combined with scaling and another NuFFT (type 2).

\paragraph{Reformulation by Gaussian Gridding \& FFT} 
The basic idea is convolution by the Gaussian... leave it for later.

For NuFFT of type 1, introducing a free parameter $\eta$, we have that
\begin{equation}
\sum_{n=1}^{N} \mathbf{f}_n e ^{i \mathbf{k} \cdot \mathbf{x}_m }  = e^{\eta k^2 / 8 \xi^2} \sum_{n=1}^{N} \mathbf{f}_n e^{-\eta k^2 / 8 \xi^2} e ^{-i (\mathbf{-k}) \cdot \mathbf{x}_m }  := e^{\eta k^2 / 8 \xi^2} \hat{H}_{\mathbf{-k}}
\end{equation}
while $\hat{H}_{\mathbf{k}}$ is the inverse Fourier transform of 
\begin{equation}
H(\mathbf{x}) = \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2}  \sum_{n=1}^N \mathbf{f}_n e^{-2 \xi^2 |\mathbf{x} - \mathbf{x}_n|_{\ast}^2 / \eta} \label{eq:gaussian_gridding_1}
\end{equation}
where $|\cdot|_{\ast}$ denotes distance to closest periodic image. (\textit{Remark from Guanchun: The distance is a little weird, I haven't checked if it's the inverse Fourier transform or not. Is it common in periodic setting?})

For the part of type 2 NuFFT, under the same parameter $\eta$, first we can simplify 
\begin{align}
\mathbf{u}^F (\mathbf{x}_m) & = \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) e^{-k^2/4\xi^2} e^{\eta k^2 / 8 \xi^2} \hat{H}_{\mathbf{-k}} e ^{-i \mathbf{k} \cdot \mathbf{x}_m} \\
%& =  \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) \hat{H}_{\mathbf{-k}} e^{- \eta k^2 / 8 \xi^2}  e ^{i (\mathbf{-k}) \cdot \mathbf{x}_n} \\
%& = \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{-k}) \hat{H}_{\mathbf{k}} e^{- \eta k^2 / 8 \xi^2}  e ^{i \mathbf{k} \cdot \mathbf{x}_n} \\
& = \frac{1}{V} \sum_{\mathbf{k} \neq 0} \hat{\tilde{H}}_{\mathbf{k}} e^{- \eta k^2 / 8 \xi^2}  e ^{i \mathbf{k} \cdot \mathbf{x}_m} 
\end{align}
with 
\begin{equation}
\hat{\tilde{H}}_{\mathbf{k}} := \mathbf{B}(\xi, \mathbf{-k}) \hat{H}_{\mathbf{k}} e^{-(1-\eta)k^2 / 4\xi^2} \label{eq:hat_tilde_h_formula}
\end{equation}
Then we denote $\tilde{H}(\mathbf{x}_i)$ as the inverse Fourier transform of $
\hat{\tilde{H}}_{\mathbf{k}}$.

According to the convolution argument, we have that
\begin{align}
\mathbf{u}^F (\mathbf{x}_m) & =  \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2}  \int_{\Omega} \tilde{H}(\mathbf{x}) e^{-2 \xi |\mathbf{x} - \mathbf{x}_m|_{\ast}^2 / \eta} \mathtt{d} \mathbf{x} \\
& \approx \sum_{\mathbf{x}_{(i)} \ \text{in equi-space grid}} \tilde{H}(\mathbf{x}_{(i)}) e^{-2 \xi |\mathbf{x}_{(i)} - \mathbf{x}_m|_{\ast}^2 / \eta} \label{eq:gaussian_gridding_2}
\end{align}
The approximation integral is spectrally accurate since the integrand is periodic.

Now the only left problem is how to compute Eq.\eqref{eq:gaussian_gridding_1} and Eq.\eqref{eq:gaussian_gridding_2}. The formula is known as \textbf{Gaussian gridding}.

\paragraph{Fast Gaussian Gridding} The idea of fast Gaussian gridding is pre-compute and store the exponential and only do necessary multiplications.

Roughly speaking, for 1D situation, we have that ($x_{(i)} = ih$)
\begin{equation}
e^{-\alpha|x_{(i)} - x_n|^2} = e^{-\alpha|ih - x_n|^2} = e^{-\alpha (ih)^2} \left(e^{2 \alpha h x_n}\right)^i e^{-\alpha x_n^2}
\end{equation}
All $e^{-\alpha (ih)^2}, e^{2 \alpha h x_n}, e^{-\alpha x_n^2}$ can be precomputed and then each time we only need to do some multiplications.

\textit{Remark from Guanchun: It's said to be 5 to 10 times faster in 2D than naive method and will perform better in higher dimension. However, I was wondering if we do the naive matrix multiplication on GPU, maybe it's still fast enough?}

\paragraph{The Description of Algorithm}
The algorithm is conducted in the following way:
\begin{enumerate}[(1)]
	\item Choose the free parameter $\xi$ and $\eta$ wisely and construct the uniform grid according to the problem.
	\item Evaluate $H(\mathbf{x})$ on the grid according to Eq.\eqref{eq:gaussian_gridding_1} with fast Gaussian gridding.
	\item Conduct FFT on $H(\mathbf{x})$ to get $\hat{H}_{\mathbf{k}}$.
	\item Apply the scaling according to Eq.\eqref{eq:hat_tilde_h_formula} to get $\hat{\tilde{H}}_{\mathbf{k}}$.
	\item Conduct iFFT on $\hat{\tilde{H}}_{\mathbf{k}}$ to get $\tilde{H}(\mathbf{x})$.
	\item Evaluate the $\mathbf{u}^F (\mathbf{x}_m)$ according to Eq.\eqref{eq:gaussian_gridding_2} with fast Gaussian gridding.
	\item Evaluate the $\mathbf{u}^R (\mathbf{x}_m)$ in real space and get the final result.
\end{enumerate}

\paragraph{Pseudo-code}
\end{document}

### 2019-05-11 report/draft.tex
Pesudocode
Add the pesudocode,  modify some typo in the draft

@@
 \begin{align}
-\mathbf{u}^F (\mathbf{x}_m) & =  \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2}  \int_{\Omega} \tilde{H}(\mathbf{x}) e^{-2 \xi |\mathbf{x} - \mathbf{x}_m|_{\ast}^2 / \eta} \mathtt{d} \mathbf{x} \\
-& \approx \sum_{\mathbf{x}_{(i)} \ \text{in equi-space grid}} \tilde{H}(\mathbf{x}_{(i)}) e^{-2 \xi |\mathbf{x}_{(i)} - \mathbf{x}_m|_{\ast}^2 / \eta} \label{eq:gaussian_gridding_2}
+\mathbf{u}^F (\mathbf{x}_m) & =  \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2}  \int_{\Omega} \tilde{H}(\mathbf{x}) e^{-2 \xi^2 |\mathbf{x} - \mathbf{x}_m|_{\ast}^2 / \eta} \mathtt{d} \mathbf{x} \\
+& \approx \frac{V}{N_{\text{grid}}} \left(\frac{2 \xi^2}{\pi \eta}\right)^{3/2} \sum_{\mathbf{x}_{(i)} \ \text{in equi-space grid}} \tilde{H}(\mathbf{x}_{(i)}) e^{-2 \xi^2 |\mathbf{x}_{(i)} - \mathbf{x}_m|_{\ast}^2 / \eta} \label{eq:gaussian_gridding_2}
 \end{align}
@@
 \paragraph{Pseudo-code}
+
 \end{document}

### 2019-05-16 report/draft.tex
Fix some typo
Fix some typo in the report

@@
 \end{equation}
-while $\hat{H}_{\mathbf{k}}$ is the inverse Fourier transform of 
+while $\hat{H}_{\mathbf{k}}$ is the Fourier transform of 
 \begin{equation}
@@
 where $|\cdot|_{\ast}$ denotes distance to closest periodic image.
-(\textit{Remark from Guanchun: The distance is a little weird, I haven't checked if it's the inverse Fourier transform or not.
+(\textit{Remark from Guanchun: The distance is a little weird, I haven't checked if it's the Fourier transform or not.
 Is it common in periodic setting?})

### 2019-05-19 src/ewald.cpp
code framework

@@ -1,0 +1,53 @@
+#include <cmath>
+#include <vector>
+#include <ctime>
+#include "ewald.h"
+
+using namespace std;
+
+void initialize(){
+  nx = 10;
+  ny = 10;
+  nz = 10;
+  Lx = 10.0;
+  Ly = 10.0;
+  Lz = 10.0;
+  eta = 1.0;
+  xi = 1,0;
+  np = 100;
+  grid = (double*)calloc(np*DIM,sizeof(double));
+  particle = (double*)calloc(np*DIM,sizeof(double));
+  strength = (double*)calloc(np*DIM,sizeof(double));
+  vel = (double*)calloc(np*DIM,sizeof(double));
+  cout << "System initialized!" << '\n';
+}
+
+void realspace(){
+}
+
+void kspace(){
+
+}
+void selfcontribution(){
+  long tt = clock();
+  double tmp = (4*xi)/sqrt(M_PI);
+  for (long i = 0; i < np; i++) {
+    vel[DIM*i+0] -= tmp*strength[DIM*i+0];
+    vel[DIM*i+1] -= tmp*strength[DIM*i+1];
+    vel[DIM*i+2] -= tmp*strength[DIM*i+2];
+  }
+  printf("Self Contribution part finished with %ds\n",(clock()-tt)*1.0/CLOCK_PER_SEC);
+
+}
+
+void writeout(){
+
+}
+
+void freeall(){
+  free(grid);
+  free(particle);
+  free(strength);
+  free(vel);
+  cout << "Dynamical variable destoyed!" << '\n';
+}

### 2019-05-19 src/ewald.h

@@ -1,0 +1,22 @@
+#ifndef EWALD_H
+#define EWALD_H
+#define DIM 3
+using namespace std;
+
+double norm(double x,double y,double z);
+
+double dp(double x,double y,double z,double xx,double yy,double zz);
+
+void initialize();
+void realspace();
+void kspace();
+void selfcontribution();
+void writeout();
+void free();
+
+int nx, ny, nz, np;
+double Lx, Ly, Lz, xi, eta;
+
+double *grid, *particle, *strength, *vel;
+
+#endif

### 2019-05-19 src/main.cpp

@@ -1,0 +1,21 @@
+#include <cmath>
+#include <vector>
+#include <ctime>
+#include "ewald.h"
+
+using namespace std;
+
+const double Pi = 3.1415927;
+
+// Main implementation
+int main(int argc, char* argv[])
+{
+  long tt = clock();
+  initialize();
+  realspace();
+  kspace();
+  selfcontribution();
+  writeout();
+  printf("Total time is %ds\n",(clock()-tt)*1.0/CLOCK_PER_SEC);
+  return 0;
+}

### 2019-05-19 src/ewald.cpp
output

@@ -1,6 +1,7 @@
 #include <cmath>
 #include <vector>
 #include <ctime>
+#include <fstream>
 #include "ewald.h"
 
 using namespace std;
@@ -19,6 +20,7 @@ void initialize(){
   particle = (double*)calloc(np*DIM,sizeof(double));
   strength = (double*)calloc(np*DIM,sizeof(double));
   vel = (double*)calloc(np*DIM,sizeof(double));
+  outputfile = "../results/vel.txt"
   cout << "System initialized!" << '\n';
 }
 
@@ -41,7 +43,17 @@ void selfcontribution(){
 }
 
 void writeout(){
-
+  ofstream output(outputfile);
+  output << "#Velocity obtained from Ewald summation" << endl;
+  output << np << endl;
+  for(long i = 0; i < np; i += 1){
+      output << i << " " << vel[DIM*i+0] << " " <<
+      vel[DIM*i+1] << " " <<
+      vel[DIM*i+2]<< "\n" ;
+    }
+  outfile.close();
+  outfile.clear();
+  printf("Write files into %s",outputfile);
 }
 
 void freeall(){

### 2019-05-19 src/ewald.h

@@ -19,4 +19,6 @@ double Lx, Ly, Lz, xi, eta;
 
 double *grid, *particle, *strength, *vel;
 
+char outputfile[256];
+
 #endif

### 2019-05-19 src/ewald.cpp
real space

@@ -20,12 +20,87 @@ void initialize(){
   particle = (double*)calloc(np*DIM,sizeof(double));
   strength = (double*)calloc(np*DIM,sizeof(double));
   vel = (double*)calloc(np*DIM,sizeof(double));
-  outputfile = "../results/vel.txt"
-  cout << "System initialized!" << '\n';
+  outputfile = "../results/vel.txt";
+  cout << "System initialized! # of particles: " << np << '\n';
+}
+
+double* realfunc(double x, double y, double z, double xi, double *st1, double *st2){
+  double r2 = x*x + y*y + z*z;
+  double r = sqrt(r2);
+  double e1 = exp(xi*xi*r2);
+  double v[3][2], tmp1[3], tmp2[3];
+  double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r,4*xi/sqrt(M_PI)*e1};
+  double *st = st1;
+  tmp1 = {
+    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2]),
+    (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
+    (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
+  };
+  st = st2;
+  tmp2 = {
+    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2]),
+    (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
+    (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
+  };
+  v =  {
+    coef[0]*tmp1[0]-coef[1]*st1[0],
+    coef[0]*tmp1[1]-coef[1]*st1[1],
+    coef[0]*tmp1[2]-coef[1]*st1[2],
+    coef[0]*tmp2[0]-coef[1]*st2[0],
+    coef[0]*tmp2[1]-coef[1]*st2[1],
+    coef[0]*tmp2[2]-coef[1]*st2[2]
+  };
+  return v;
+
+
+
 }
 
 void realspace(){
+  double rx, ry, rz;
+  double *v;
+  long tt = clock();
+  for (int i = 0; i < np; i++){
+    for (int j = i+1; j < np; j++){
+      for (int px = -repeat_x; px < repeat_x; px++){
+        for (int py = -repeat_y; py < repeat_y; py++){
[…]

### 2019-05-19 src/main.cpp

@@ -5,9 +5,7 @@
 
 using namespace std;
 
-const double Pi = 3.1415927;
 
-// Main implementation
 int main(int argc, char* argv[])
 {
   long tt = clock();

### 2019-05-20 src/ewald_Guanchun_Gaussian_Gridding.cpp
Gaussian Gridding function
Add the code for Gaussian Gridding

@@ -1,0 +1,175 @@
+#include <cmath>
+#include <vector>
+#include <ctime>
+#include <fstream>
+#include "ewald.h"
+
+using namespace std;
+
+void initialize(){
+  nx = 100;
+  ny = 100;
+  nz = 100;
+  Lx = 1.0;
+  Ly = 1.0;
+  Lz = 1.0;
+  eta = 1.0;
+  xi = 5;
+  np = 100;
+  // grid = (double*)calloc(np*DIM,sizeof(double));
+  particle = (double*) calloc(np*DIM,sizeof(double));
+  strength = (double*) calloc(np*DIM,sizeof(double));
+  vel = (double*) calloc(np*DIM,sizeof(double));
+  // outputfile = "../results/vel.txt"
+  // cout << "System initialized!" << '\n';
+}
+
+double* Gaussian_Gridding_type1(int Px, int Py, int Pz){
+  double* H = (double*) calloc(DIM*nx*ny*nz, sizeof(double));
+  double hx = Lx / nx, hy = Ly / ny, hz = Lz / nz;
+  double hx_sq = hx * hx, hy_sq = hy * hy, hz_sq = hy * hy;
+  int ig, jg, kg;
+  double a = - 2 * xi * xi / eta;
+  double xp, yp, zp, xp_o, yp_o, zp_o;
+  int ip, jp, kp;
+  double* E3_x = (double*) calloc(Px+1, sizeof(double));
+  double* E3_y = (double*) calloc(Py+1, sizeof(double));
+  double* E3_z = (double*) calloc(Pz+1, sizeof(double));
+  double E1_x, E1_y, E1_z, E2_x, E2_y, E2_z;
+  double* E2_xl = (double*) calloc(2*Px, sizeof(double));
+  double* E2_yl = (double*) calloc(2*Py, sizeof(double));
+  double* E2_zl = (double*) calloc(2*Pz, sizeof(double));
+  double V0, Vx, Vy, Vz;
+  for (long i = 0; i <= Px; i++) {
+      E3_x[i] = exp(-a*i*i*hx_sq);
+  }
+  for (long i = 0; i <= Py; i++) {
+      E3_y[i] = exp(-a*i*i*hy_sq);
+  }
+  for (long i = 0; i <= Pz; i++) {
+      E3_z[i] = exp(-a*i*i*hz_sq);
+  }
[…]

### 2019-05-20 src/ewald.cpp
kspace

@@ -2,6 +2,7 @@
 #include <vector>
 #include <ctime>
 #include <fstream>
+#include <complex>
 #include "ewald.h"
 
 using namespace std;
@@ -16,6 +17,9 @@ void initialize(){
   eta = 1.0;
   xi = 1,0;
   np = 100;
+  px = 7;
+  py = 7;
+  pz = 7;
   grid = (double*)calloc(np*DIM,sizeof(double));
   particle = (double*)calloc(np*DIM,sizeof(double));
   strength = (double*)calloc(np*DIM,sizeof(double));
@@ -23,6 +27,7 @@ void initialize(){
   outputfile = "../results/vel.txt";
   cout << "System initialized! # of particles: " << np << '\n';
 }
+
 
 double* realfunc(double x, double y, double z, double xi, double *st1, double *st2){
   double r2 = x*x + y*y + z*z;
@@ -101,8 +106,160 @@ void realspace(){
   printf("Real space part finished with %ds\n",(clock()-tt)*1.0/CLOCK_PER_SEC);
 }
 
+double* Gaussian_Gridding_type1(){
+
+}
+
+double* Gaussian_Gridding_type2(double *Hx){
+
+}
+
+
+double* Gaussian_Gridding_type1(int Px, int Py, int Pz){
+  double* H = (double*) calloc(DIM*nx*ny*nz, sizeof(double));
+  double hx = Lx / nx, hy = Ly / ny, hz = Lz / nz;
+  double hx_sq = hx * hx, hy_sq = hy * hy, hz_sq = hy * hy;
+  int ig, jg, kg;
+  double a = - 2 * xi * xi / eta;
+  double xp, yp, zp, xp_o, yp_o, zp_o;
+  int ip, jp, kp;
+  double* E3_x = (double*) calloc(Px+1, sizeof(double));
+  double* E3_y = (double*) calloc(Py+1, sizeof(double));
+  double* E3_z = (double*) calloc(Pz+1, sizeof(double));
+  double E1_x, E1_y, E1_z, E2_x, E2_y, E2_z;
+  double* E2_xl = (double*) calloc(2*Px, sizeof(double));
[…]

### 2019-05-20 src/ewald.h

@@ -14,7 +14,7 @@ void selfcontribution();
 void writeout();
 void free();
 
-int nx, ny, nz, np;
+int nx, ny, nz, np, px, py, pz;
 double Lx, Ly, Lz, xi, eta;
 
 double *grid, *particle, *strength, *vel;

### 2019-05-20 src/ewald.cpp
kspace1

@@ -14,8 +14,8 @@ void initialize(){
   Lx = 10.0;
   Ly = 10.0;
   Lz = 10.0;
-  eta = 1.0;
-  xi = 1,0;
+  eta = 0.5;
+  xi = 1.0;
   np = 100;
   px = 7;
   py = 7;
@@ -76,13 +76,13 @@ void realspace(){
                 ry = particle[DIM*j+1]-particle[DIM*i+1];
                 rz = particle[DIM*j+2]-particle[DIM*i+2];
                 v = realfunc(rx, ry, rz, xi, &(strength[DIM*i]), &(strength[DIM*j]));
-                vel[DIM*i+0] += v[0];
-                vel[DIM*i+1] += v[1];
-                vel[DIM*i+2] += v[2];
+                vel[DIM*i+0] += v[3];
+                vel[DIM*i+1] += v[4];
+                vel[DIM*i+2] += v[5];
 
-                vel[DIM*j+0] += v[3];
-                vel[DIM*j+1] += v[4];
-                vel[DIM*j+2] += v[5];
+                vel[DIM*j+0] += v[0];
+                vel[DIM*j+1] += v[1];
+                vel[DIM*j+2] += v[2];
               }
             }
             else{
@@ -90,13 +90,13 @@ void realspace(){
               ry = particle[DIM*j+1]+Ly*py-particle[DIM*i+1];
               rz = particle[DIM*j+2]+Lz*pz-particle[DIM*i+2];
               v = realfunc(rx, ry, rz, xi, &(strength[DIM*i]), &(strength[DIM*j]));
-              vel[DIM*i+0] += v[0];
-              vel[DIM*i+1] += v[1];
-              vel[DIM*i+2] += v[2];
+              vel[DIM*i+0] += v[3];
+              vel[DIM*i+1] += v[4];
+              vel[DIM*i+2] += v[5];
 
-              vel[DIM*j+0] += v[3];
-              vel[DIM*j+1] += v[4];
-              vel[DIM*j+2] += v[5];
+              vel[DIM*j+0] += v[0];
[…]

### 2019-05-20 src/ewald.cpp
Add direct function part

@@ -37,13 +37,13 @@ double* realfunc(double x, double y, double z, double xi, double *st1, double *s
   double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r,4*xi/sqrt(M_PI)*e1};
   double *st = st1;
   tmp1 = {
-    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2]),
+    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2],
     (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
     (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
   };
   st = st2;
   tmp2 = {
-    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2]),
+    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2],
     (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
     (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
   };

### 2019-05-20 src/ewald_Guanchun_Gaussian_Gridding.cpp

@@ -24,6 +24,72 @@ void initialize(){
   // cout << "System initialized!" << '\n';
 }
 
+double* directfunc(double x, double y, double z, double xi, double *st1, double *st2){
+  double r2 = x*x + y*y + z*z;
+  double r = sqrt(r2); double r_inv = 1/r; 
+  double r3_inv = 1 / (r*r*r);
+  double v[3][2];
+  double tmp1 = 0.0, tmp2 = 0.0;
+  tmp1 = x * st1[0] + y * st1[1] + z * st1[2]
+  tmp2 = x * st2[0] + y * st2[1] + z * st2[2]
+  v =  {
+    r_inv*st2[0] + r3_inv*tmp2*x,
+    r_inv*st2[1] + r3_inv*tmp2*y,
+    r_inv*st2[2] + r3_inv*tmp2*z,
+    r_inv*st1[0] + r3_inv*tmp1*x,
+    r_inv*st1[1] + r3_inv*tmp1*y,
+    r_inv*st1[2] + r3_inv*tmp1*z,
+  };
+  return v;
+}
+
+double* direct_compute(int repeat_x, int repeat_y, int repeat_z){
+  double *vel_direct = (double*) calloc(np*DIM,sizeof(double));
+  double rx, ry, rz;
+  double *v;
+  long tt = clock();
+  for (int i = 0; i < np; i++){
+    for (int j = i+1; j < np; j++){
+      for (int px = -repeat_x; px < repeat_x; px++){
+        for (int py = -repeat_y; py < repeat_y; py++){
+          for (int pz = -repeat_z; pz < repeat_z; pz++){
+            if (px == 0 && py == 0 && pz == 0){
+              if (i != j) {
+                rx = particle[DIM*j+0]-particle[DIM*i+0];
+                ry = particle[DIM*j+1]-particle[DIM*i+1];
+                rz = particle[DIM*j+2]-particle[DIM*i+2];
+                v = directfunc(rx, ry, rz, xi, &(strength[DIM*i]), &(strength[DIM*j]));
+                vel_direct[DIM*i+0] += v[0];
+                vel_direct[DIM*i+1] += v[1];
+                vel_direct[DIM*i+2] += v[2];
+
+                vel_direct[DIM*j+0] += v[3];
+                vel_direct[DIM*j+1] += v[4];
+                vel_direct[DIM*j+2] += v[5];
+              }
+            }
[…]

### 2019-05-20 src/ewald.cpp
Modify the Ewald cpp

@@ -103,12 +103,13 @@ void realspace(){
       }
     }
   }
-  printf("Real space part finished with %ds\n",(clock()-tt)*1.0/CLOCK_PER_SEC);
+  printf("Real space part finished with %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
 }
 
 
 
 double* Gaussian_Gridding_type1(){
+  long tt = clock();
   double* H = (double*) calloc(DIM*nx*ny*nz, sizeof(double));
   double hx = Lx / nx, hy = Ly / ny, hz = Lz / nz;
   double hx_sq = hx * hx, hy_sq = hy * hy, hz_sq = hy * hy;
@@ -170,10 +171,13 @@ double* Gaussian_Gridding_type1(){
       }
     }
   }
+  printf("Gaussian_Gridding_type1 finished with %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
   return H;
 }
 
-double* Gaussian_Gridding_type2(double* H){
+void Gaussian_Gridding_type2(double* H){
+  long tt = clock();
+  double scale_factor = hx*hy*hz * pow(2*xi*xi/(M_PI*eta), 1.5);
   double* vel_F = (double*) calloc(np*DIM, sizeof(double));
   double hx = Lx / nx, hy = Ly / ny, hz = Lz / nz;
   double hx_sq = hx * hx, hy_sq = hy * hy, hz_sq = hy * hy;
@@ -229,13 +233,13 @@ double* Gaussian_Gridding_type2(double* H){
           Vz = Vy * E2_zl[k+pz-1] * E3_z[abs(k)];
           ig = (ip+i+nx) % nx; jg = (jp+j+ny) % ny; kg = (kp+k+nz) % nz;
           for (long m = 0; m < DIM; m++){
-            vel_F[DIM*n+m] += Vz * H[kg + ny*(jg + nz*(ig + m*nx))];
+            vel[DIM*n+m] += scale_factor * Vz * H[kg + ny*(jg + nz*(ig + m*nx))];
           }
         }
       }
     }
   }
-  return vel_F;
+  printf("Gaussian_Gridding_type2 finished with %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
 }
 
 

### 2019-05-20 src/ewald.cpp
local

@@ -293,9 +293,10 @@ void kspace(){
     }
   }
   Hx = IFFT3D(Hx_tilde);
-  double *v = Gaussian_Gridding_type2(Hx);
+  Gaussian_Gridding_type2(Hx);
   printf("k-pace part finished with %ds\n",(clock()-tt)*1.0/CLOCK_PER_SEC);
 }
+
 void selfcontribution(){
   long tt = clock();
   double tmp = (4*xi)/sqrt(M_PI);

### 2019-05-20 src/ewald.cpp
merged

@@ -37,13 +37,13 @@ double* realfunc(double x, double y, double z, double xi, double *st1, double *s
   double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r,4*xi/sqrt(M_PI)*e1};
   double *st = st1;
   tmp1 = {
-    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2],
+    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2]),
     (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
     (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
   };
   st = st2;
   tmp2 = {
-    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2],
+    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2]),
     (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
     (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
   };
@@ -103,13 +103,12 @@ void realspace(){
       }
     }
   }
-  printf("Real space part finished with %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
+  printf("Real space part finished with %ds\n",(clock()-tt)*1.0/CLOCK_PER_SEC);
 }
 
 
 
 double* Gaussian_Gridding_type1(){
-  long tt = clock();
   double* H = (double*) calloc(DIM*nx*ny*nz, sizeof(double));
   double hx = Lx / nx, hy = Ly / ny, hz = Lz / nz;
   double hx_sq = hx * hx, hy_sq = hy * hy, hz_sq = hy * hy;
@@ -171,13 +170,10 @@ double* Gaussian_Gridding_type1(){
       }
     }
   }
-  printf("Gaussian_Gridding_type1 finished with %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
   return H;
 }
 
-void Gaussian_Gridding_type2(double* H){
-  long tt = clock();
-  double scale_factor = hx*hy*hz * pow(2*xi*xi/(M_PI*eta), 1.5);
+double* Gaussian_Gridding_type2(double* H){
   double* vel_F = (double*) calloc(np*DIM, sizeof(double));
[…]

### 2019-05-20 src/ewald.cpp
cufft

@@ -33,32 +33,23 @@ double* realfunc(double x, double y, double z, double xi, double *st1, double *s
   double r2 = x*x + y*y + z*z;
   double r = sqrt(r2);
   double e1 = exp(xi*xi*r2);
-  double v[3][2], tmp1[3], tmp2[3];
+  double v[6], tmp1[3], tmp2[3];
   double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r,4*xi/sqrt(M_PI)*e1};
   double *st = st1;
-  tmp1 = {
-    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2],
-    (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
-    (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
-  };
+  tmp1[0] = (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2];
+  tmp1[1] = (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2];
+  tmp1[2] = (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2];
   st = st2;
-  tmp2 = {
-    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2],
-    (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
-    (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
-  };
-  v =  {
-    coef[0]*tmp1[0]-coef[1]*st1[0],
-    coef[0]*tmp1[1]-coef[1]*st1[1],
-    coef[0]*tmp1[2]-coef[1]*st1[2],
-    coef[0]*tmp2[0]-coef[1]*st2[0],
-    coef[0]*tmp2[1]-coef[1]*st2[1],
-    coef[0]*tmp2[2]-coef[1]*st2[2]
-  };
+  tmp2[0] = (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2];
+  tmp2[1] = (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2];
+  tmp2[2] = (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2];
[…]

### 2019-05-20 src/ewald.cpp
cufft buggy

@@ -233,14 +233,16 @@ void Gaussian_Gridding_type2(double* H){
   printf("Gaussian_Gridding_type2 finished with %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
 }
 
-complex<double> FFT3D(double *H){
+complex<double>* FFT3D(double *H){
   cufftHandle plan;
   cufftDoubleReal *data;
   cufftDoubleComplex *data1;
+  complex<double> *odata;
+  Malloc((void**)&odata, sizeof(complex<double>)*nx*ny*(nz/2+1)*3);
   int n[DIM] = {nx, ny, nz};
   cudaMalloc((void**)&data, sizeof(cufftDoubleReal)*nx*ny*nz*3);
   cudaMalloc((void**)&data1, sizeof(cufftDoubleComplex)*nx*ny*(nz/2+1)*3);
-  cudaMemcpy(data,H,nx*ny*nz*3*sizeof(cufftDoubleReal));
+  cudaMemcpy(data,H,nx*ny*nz*3*sizeof(cufftDoubleReal),cudaMemcpyHostToDevice);
   if (cudaGetLastError() != cudaSuccess){
     fprintf(stderr, "Cuda error: Failed to allocate\n");
     return;
@@ -248,27 +250,63 @@ complex<double> FFT3D(double *H){
   /* Create a 3D FFT plan. */
   if (cufftPlanMany(&plan, DIM, n,
     NULL, 1, nx*ny*nz, // *inembed, istride, idist
-    NULL, 1, nx*ny*nz, // *onembed, ostride, odist
+    NULL, 1, nx*ny*(nz/2+1), // *onembed, ostride, odist
     CUFFT_D2Z, 3) != CUFFT_SUCCESS){
       fprintf(stderr, "CUFFT error: Plan creation failed");
       return;
     }
     /* Use the CUFFT plan to transform the signal in place. */
     if (cufftExecD2Z(plan, data, data1) != CUFFT_SUCCESS){
-      fprintf(stderr, "CUFFT error: ExecC2C Forward failed");
+      fprintf(stderr, "CUFFT error: ExecD2Z Forward failed");
       return;
     }
     if (cudaDeviceSynchronize() != cudaSuccess){
       fprintf(stderr, "Cuda error: Failed to synchronize\n");
       return;
     }
[…]

### 2019-05-20 src/ewald.cpp
normalization of ifft

@@ -306,6 +306,15 @@ double* IFFT3D(complex<double> *H){
     cufftDestroy(plan);
     cudaFree(data);
     cudaFree(data1);
+    for (int idim = 0; idim<3; idim++){
+      for (int i = 0; i<nx; i++){
+        for (int j = 0; j<ny; j++){
+          for (int k = 0; k<nz; k++){
+            odata[idim*(nx*ny*nz)+i*(ny*nz)+j*nz+k]/=(nx*ny*nz);
+          }
+        }
+      }
+    }
     return odata;
 }
 

### 2019-05-20 src/ewald.cu
return pointer to local variables

@@ -2,7 +2,10 @@
 #include <vector>
 #include <ctime>
 #include <fstream>
+#include <iostream>
 #include <complex>
+#include <cufft.h>
+#include <cstdio>
 #include "ewald.h"
 
 using namespace std;
@@ -20,6 +23,9 @@ void initialize(){
   px = 7;
   py = 7;
   pz = 7;
+  repeat_x = 2;
+  repeat_y = 2;
+  repeat_z = 2;
   grid = (double*)calloc(np*DIM,sizeof(double));
   particle = (double*)calloc(np*DIM,sizeof(double));
   strength = (double*)calloc(np*DIM,sizeof(double));
@@ -34,7 +40,7 @@ double* realfunc(double x, double y, double z, double xi, double *st1, double *s
   double r = sqrt(r2);
   double e1 = exp(xi*xi*r2);
   double v[6], tmp1[3], tmp2[3];
-  double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r,4*xi/sqrt(M_PI)*e1};
+  double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r),4*xi/sqrt(M_PI)*e1};
   double *st = st1;
   tmp1[0] = (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2];
   tmp1[1] = (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2];
@@ -168,9 +174,9 @@ double* Gaussian_Gridding_type1(){
 
 void Gaussian_Gridding_type2(double* H){
   long tt = clock();
-  double scale_factor = hx*hy*hz * pow(2*xi*xi/(M_PI*eta), 1.5);
   double* vel_F = (double*) calloc(np*DIM, sizeof(double));
   double hx = Lx / nx, hy = Ly / ny, hz = Lz / nz;
+  double scale_factor = hx*hy*hz * pow(2*xi*xi/(M_PI*eta), 1.5);
   double hx_sq = hx * hx, hy_sq = hy * hy, hz_sq = hy * hy;
   int ig, jg, kg;
   double a = - 2 * xi * xi / eta;
@@ -238,14 +244,14 @@ complex<double>* FFT3D(double *H){
   cufftDoubleReal *data;
   cufftDoubleComplex *data1;
   complex<double> *odata;
[…]

### 2019-05-20 src/ewald.h

@@ -14,11 +14,11 @@ void selfcontribution();
 void writeout();
 void free();
 
-int nx, ny, nz, np, px, py, pz;
+int nx, ny, nz, np, px, py, pz, repeat_x, repeat_y, repeat_z;
 double Lx, Ly, Lz, xi, eta;
 
 double *grid, *particle, *strength, *vel;
 
-char outputfile[256];
+string outputfile;
 
 #endif

### 2019-05-20 src/main.cpp

@@ -1,6 +1,8 @@
 #include <cmath>
 #include <vector>
 #include <ctime>
+#include <cstdio>
+#include <string>
 #include "ewald.h"
 
 using namespace std;
@@ -14,6 +16,6 @@ int main(int argc, char* argv[])
   kspace();
   selfcontribution();
   writeout();
-  printf("Total time is %ds\n",(clock()-tt)*1.0/CLOCK_PER_SEC);
+  printf("Total time is %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
   return 0;
 }

### 2019-05-20 src/ewald.cu
runable version beta 1.0

@@ -35,11 +35,11 @@ void initialize(){
 }
 
 
-double* realfunc(double x, double y, double z, double xi, double *st1, double *st2){
+void realfunc(double x, double y, double z, double xi, double *st1, double *st2, double *v){
   double r2 = x*x + y*y + z*z;
   double r = sqrt(r2);
   double e1 = exp(xi*xi*r2);
-  double v[6], tmp1[3], tmp2[3];
+  double tmp1[3], tmp2[3];
   double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r),4*xi/sqrt(M_PI)*e1};
   double *st = st1;
   tmp1[0] = (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2];
@@ -55,12 +55,12 @@ double* realfunc(double x, double y, double z, double xi, double *st1, double *s
   v[3] = coef[0]*tmp2[0]-coef[1]*st2[0];
   v[4] = coef[0]*tmp2[1]-coef[1]*st2[1];
   v[5] = coef[0]*tmp2[2]-coef[1]*st2[2];
-  return v;
+  return;
 }
 
 void realspace(){
   double rx, ry, rz;
-  double *v;
+  double v[6];
   long tt = clock();
   for (int i = 0; i < np; i++){
     for (int j = i+1; j < np; j++){
@@ -72,7 +72,7 @@ void realspace(){
                 rx = particle[DIM*j+0]-particle[DIM*i+0];
                 ry = particle[DIM*j+1]-particle[DIM*i+1];
                 rz = particle[DIM*j+2]-particle[DIM*i+2];
-                v = realfunc(rx, ry, rz, xi, &(strength[DIM*i]), &(strength[DIM*j]));
+                realfunc(rx, ry, rz, xi, &(strength[DIM*i]), &(strength[DIM*j]), v);
                 vel[DIM*i+0] += v[3];
                 vel[DIM*i+1] += v[4];
                 vel[DIM*i+2] += v[5];
@@ -86,7 +86,7 @@ void realspace(){
               rx = particle[DIM*j+0]+Lx*px-particle[DIM*i+0];
               ry = particle[DIM*j+1]+Ly*py-particle[DIM*i+1];
               rz = particle[DIM*j+2]+Lz*pz-particle[DIM*i+2];
[…]

### 2019-05-20 src/ewald.h

@@ -3,9 +3,6 @@
 #define DIM 3
 using namespace std;
 
-double norm(double x,double y,double z);
-
-double dp(double x,double y,double z,double xx,double yy,double zz);
 
 void initialize();
 void realspace();
@@ -14,11 +11,11 @@ void selfcontribution();
 void writeout();
 void free();
 
-int nx, ny, nz, np, px, py, pz, repeat_x, repeat_y, repeat_z;
-double Lx, Ly, Lz, xi, eta;
+extern int nx, ny, nz, np, px, py, pz, repeat_x, repeat_y, repeat_z;
+extern double Lx, Ly, Lz, xi, eta;
 
-double *grid, *particle, *strength, *vel;
+extern double *grid, *particle, *strength, *vel;
 
-string outputfile;
+extern string outputfile;
 
 #endif

### 2019-05-20 src/global.cpp

@@ -1,0 +1,9 @@
+#include <string>
+#include "ewald.h"
+
+int nx, ny, nz, np, px, py, pz, repeat_x, repeat_y, repeat_z;
+double Lx, Ly, Lz, xi, eta;
+
+double *grid, *particle, *strength, *vel;
+
+string outputfile;

### 2019-05-20 src/ewald.cu
runable version beta 1.1

@@ -6,11 +6,13 @@
 #include <complex>
 #include <cufft.h>
 #include <cstdio>
+#include <stdlib.h>
 #include "ewald.h"
 
 using namespace std;
 
 void initialize(){
+  srand((unsigned int)clock());
   nx = 10;
   ny = 10;
   nz = 10;
@@ -30,6 +32,14 @@ void initialize(){
   particle = (double*)calloc(np*DIM,sizeof(double));
   strength = (double*)calloc(np*DIM,sizeof(double));
   vel = (double*)calloc(np*DIM,sizeof(double));
+  for (int i = 0; i<np; i++){
+    particle[DIM*i+0] = rand()*1.0/RAND_MAX*Lx;
+    particle[DIM*i+1] = rand()*1.0/RAND_MAX*Ly;
+    particle[DIM*i+2] = rand()*1.0/RAND_MAX*Lz;
+    strength[DIM*i+0] = 1.0;
+    strength[DIM*i+1] = 1.0;
+    strength[DIM*i+2] = 1.0;
+  }
   outputfile = "../results/vel.txt";
   cout << "System initialized! # of particles: " << np << '\n';
 }
@@ -38,7 +48,7 @@ void initialize(){
 void realfunc(double x, double y, double z, double xi, double *st1, double *st2, double *v){
   double r2 = x*x + y*y + z*z;
   double r = sqrt(r2);
-  double e1 = exp(xi*xi*r2);
+  double e1 = exp(-xi*xi*r2);
   double tmp1[3], tmp2[3];
   double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r),4*xi/sqrt(M_PI)*e1};
   double *st = st1;
@@ -100,7 +110,7 @@ void realspace(){
       }
     }
   }
-  printf("Real space part finished with %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
+  printf("Real space part finished with %f(s)\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
 }
 
 
@@ -167,7 +177,7 @@ void Gaussian_Gridding_type1(double *H){
       }
     }
   }
-  printf("Gaussian_Gridding_type1 finished with %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
[…]

### 2019-05-20 src/main.cpp

@@ -16,6 +16,6 @@ int main(int argc, char* argv[])
   kspace();
   selfcontribution();
   writeout();
-  printf("Total time is %ds\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
+  printf("Total time is %f(s)\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
   return 0;
 }

### 2019-05-20 src/main.cpp
compile

@@ -7,7 +7,8 @@
 
 using namespace std;
 
-
+// nvcc -std=c++11 -O0 -g  main.cpp ewald.cu global.cpp -lcufft -o ewald
+// nvcc -std=c++11 -O3   main.cpp ewald.cu global.cpp -lcufft -o ewald
 int main(int argc, char* argv[])
 {
   long tt = clock();

### 2019-05-20 src/ewald.cu
1

@@ -52,31 +52,6 @@ void realfunc(double x, double y, double z, double xi, double *st1, double *st2,
   double tmp1[3], tmp2[3];
   double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r),4*xi/sqrt(M_PI)*e1};
   double *st = st1;
-<<<<<<< HEAD:src/ewald.cpp
-  tmp1 = {
-    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2]),
-    (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
-    (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
-  };
-  st = st2;
-  tmp2 = {
-    (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2]),
-    (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2],
-    (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2]
-  };
-  v =  {
-    coef[0]*tmp1[0]-coef[1]*st1[0],
-    coef[0]*tmp1[1]-coef[1]*st1[1],
-    coef[0]*tmp1[2]-coef[1]*st1[2],
-    coef[0]*tmp2[0]-coef[1]*st2[0],
-    coef[0]*tmp2[1]-coef[1]*st2[1],
-    coef[0]*tmp2[2]-coef[1]*st2[2]
-  };
-  return v;
-
-
-
-=======
   tmp1[0] = (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2];
   tmp1[1] = (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2];
   tmp1[2] = (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2];
@@ -91,7 +66,6 @@ void realfunc(double x, double y, double z, double xi, double *st1, double *st2,
   v[4] = coef[0]*tmp2[1]-coef[1]*st2[1];
   v[5] = coef[0]*tmp2[2]-coef[1]*st2[2];
   return;
->>>>>>> e65a0d6e4980fecf0048be87de70f58e3b739fe3:src/ewald.cu
 }
 
 void realspace(){
@@ -136,22 +110,13 @@ void realspace(){
       }
     }
   }
[…]

### 2019-05-20 src/ewald.cu
free gaussian grid

@@ -178,12 +178,13 @@ void Gaussian_Gridding_type1(double *H){
     }
   }
   printf("Gaussian_Gridding_type1 finished with %f(s)\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
+  free(E3_x);free(E3_y);free(E3_z);
+  free(E2_xl);free(E2_yl);free(E2_zl);
   return;
 }
 
 void Gaussian_Gridding_type2(double* H){
   long tt = clock();
-  double* vel_F = (double*) calloc(np*DIM, sizeof(double));
   double hx = Lx / nx, hy = Ly / ny, hz = Lz / nz;
   double scale_factor = hx*hy*hz * pow(2*xi*xi/(M_PI*eta), 1.5);
   double hx_sq = hx * hx, hy_sq = hy * hy, hz_sq = hz * hz;
@@ -214,7 +215,6 @@ void Gaussian_Gridding_type2(double* H){
     zp = particle[DIM*n+2];
     ip = xp/hx; jp = yp/hy; kp = zp/hz;
     xp_o = xp - ip*hx; yp_o = yp - jp*hy; zp_o = zp - kp*hz;
-
     E1_x = exp(-a*xp_o*xp_o);
     E1_y = exp(-a*yp_o*yp_o);
     E1_z = exp(-a*zp_o*zp_o);
@@ -239,13 +239,15 @@ void Gaussian_Gridding_type2(double* H){
           Vz = Vy * E2_zl[k+pz-1] * E3_z[abs(k)];
           ig = (ip+i+nx) % nx; jg = (jp+j+ny) % ny; kg = (kp+k+nz) % nz;
           for (long m = 0; m < DIM; m++){
-            vel_F[DIM*n+m] += Vz * H[kg + ny*(jg + nz*(ig + m*nx))];
+            vel[DIM*n+m] += scale_factor * Vz * H[kg + ny*(jg + nz*(ig + m*nx))];
           }
         }
       }
     }
   }
   printf("Gaussian_Gridding_type2 finished with %f(s)\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
+  free(E3_x);free(E3_y);free(E3_z);
+  free(E2_xl);free(E2_yl);free(E2_zl);
 }
 
 void FFT3D(double *H, complex<double> *odata){

### 2019-05-21 src/ewald.cu
OpenMP real space

@@ -7,24 +7,25 @@
 #include <cufft.h>
 #include <cstdio>
 #include <stdlib.h>
+#include <omp.h>
 #include "ewald.h"
 
 using namespace std;
 
 void initialize(){
-  srand((unsigned int)clock());
-  nx = 10;
-  ny = 10;
-  nz = 10;
-  Lx = 10.0;
-  Ly = 10.0;
-  Lz = 10.0;
-  eta = 0.5;
-  xi = 1.0;
-  np = 100;
-  px = 7;
-  py = 7;
-  pz = 7;
+  srand((unsigned int) 100005);
+  nx = 20;
+  ny = 20;
+  nz = 20;
+  Lx = 2.0;
+  Ly = 2.0;
+  Lz = 2.0;
+  eta = 1.15;
+  xi = 10;
+  np = 16;
+  px = 8;
+  py = 8;
+  pz = 8;
   repeat_x = 2;
   repeat_y = 2;
   repeat_z = 2;
@@ -40,7 +41,7 @@ void initialize(){
     strength[DIM*i+1] = 1.0;
     strength[DIM*i+2] = 1.0;
   }
-  outputfile = "../results/vel.txt";
+  outputfile = "../results/vel2.txt";
   cout << "System initialized! # of particles: " << np << '\n';
 }
 
@@ -67,6 +68,22 @@ void realfunc(double x, double y, double z, double xi, double *st1, double *st2,
   v[5] = coef[0]*tmp2[2]-coef[1]*st2[2];
   return;
 }
+
+void realfuncOMP(double x, double y, double z, double xi, double *st, double *v){
+  double r2 = x*x + y*y + z*z;
+  double r = sqrt(r2);
+  double e1 = exp(-xi*xi*r2);
+  double tmp1[3];
+  double coef[2] = {2*(xi*e1/sqrt(M_PI)/r2+erfc(xi*r)/2/r2/r),4*xi/sqrt(M_PI)*e1};
+  tmp1[0] = (r2+x*x)*st[0]+(x*y)*st[1]+(x*z)*st[2];
+  tmp1[1] = (y*x)*st[0]+(r2+y*y)*st[1]+(y*z)*st[2];
+  tmp1[2] = (z*x)*st[0]+(z*y)*st[1]+(r2+z*z)*st[2];
+  v[0] = coef[0]*tmp1[0]-coef[1]*st[0];
[…]

### 2019-05-21 src/ewald.h

@@ -6,6 +6,7 @@ using namespace std;
 
 void initialize();
 void realspace();
+void realspaceOMP(int num_threads);
 void kspace();
 void selfcontribution();
 void writeout();

### 2019-05-21 src/main.cpp

@@ -3,17 +3,21 @@
 #include <ctime>
 #include <cstdio>
 #include <string>
+#include <iostream>
 #include "ewald.h"
 
 using namespace std;
 
 // nvcc -std=c++11 -O0 -g  main.cpp ewald.cu global.cpp -lcufft -o ewald
 // nvcc -std=c++11 -O3   main.cpp ewald.cu global.cpp -lcufft -o ewald
-int main(int argc, char* argv[])
-{
+int main(int argc, char* argv[]){
+  int num_threads = 1;
+  cout << "Please input num of threads(default=1): " << endl;
+	cin >> num_threads;
   long tt = clock();
   initialize();
-  realspace();
+  // realspace();
+  realspaceOMP(num_threads);
   kspace();
   selfcontribution();
   writeout();

### 2019-05-21 src/ewald.cu
omp

@@ -8,24 +8,27 @@
 #include <cstdio>
 #include <stdlib.h>
 #include <omp.h>
+#include <chrono>
 #include "ewald.h"
+#include "utils.h"
 
 using namespace std;
+using namespace chrono;
 
 void initialize(){
   srand((unsigned int) 100005);
-  nx = 20;
-  ny = 20;
-  nz = 20;
+  nx = 64;
+  ny = 64;
+  nz = 64;
   Lx = 2.0;
   Ly = 2.0;
   Lz = 2.0;
   eta = 1.15;
-  xi = 10;
-  np = 16;
-  px = 8;
-  py = 8;
-  pz = 8;
+  xi = 12;
+  np = 2048;
+  px = 24;
+  py = 24;
+  pz = 24;
   repeat_x = 2;
   repeat_y = 2;
   repeat_z = 2;
@@ -88,7 +91,8 @@ void realfuncOMP(double x, double y, double z, double xi, double *st, double *v)
 void realspace(){
   double rx, ry, rz;
   double v[6];
-  long tt = clock();
+  Timer tt;
+  tt.tic();
   for (int i = 0; i < np; i++){
     for (int j = i+1; j < np; j++){
       for (int px = -repeat_x; px < repeat_x; px++){
@@ -127,7 +131,7 @@ void realspace(){
       }
     }
   }
-  printf("Real space part finished with %f(s)\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
+  printf("Real space part finished with %f(s)\n",tt.toc());
 }
 
 
@@ -139,10 +143,13 @@ void realspaceOMP(int num_threads){
 	cout << "Use " << num_threads << " threads" << endl;
 	#endif
   double rx, ry, rz;
-  double v[3];
-  long tt = clock();
-  #pragma omp parallel for
+  double tt = omp_get_wtime();
+  #pragma omp parallel private(rx,ry,rz)
+  {
+  #pragma omp for
   for (int i = 0; i < np; i++){
+    // printf("i=%d, from thread = %d\n", i, omp_get_thread_num());
+    double v[3];
     for (int j = 0; j < np; j++){
       for (int px = -repeat_x; px < repeat_x; px++){
[…]

### 2019-05-21 src/ewald.h

@@ -8,6 +8,7 @@ void initialize();
 void realspace();
 void realspaceOMP(int num_threads);
 void kspace();
+void kspaceParallel();
 void selfcontribution();
 void writeout();
 void free();

### 2019-05-21 src/main.cpp

@@ -15,12 +15,20 @@ int main(int argc, char* argv[]){
   cout << "Please input num of threads(default=1): " << endl;
 	cin >> num_threads;
   long tt = clock();
+  cout << "\n---------------initialize---------------" << endl;
   initialize();
-  // realspace();
+  cout << "\n---------------Real Space---------------" << endl;
+  realspace();
+  cout << "\n---------------Real Space OMP---------------" << endl;
   realspaceOMP(num_threads);
+  cout << "\n---------------K-Space---------------" << endl;
   kspace();
+  cout << "\n---------------K-Space Parallel---------------" << endl;
+  kspaceParallel();
+  cout << "\n---------------Self Contribution---------------" << endl;
   selfcontribution();
   writeout();
+  cout << "\n---------------In Total---------------" << endl;
   printf("Total time is %f(s)\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
   return 0;
 }

### 2019-05-21 report/draft.tex

@@
 
+\paragraph{Error estimation}
+For k-space, the error comes from two parts: the truncation error in the k-space and the quadrature error to get the velocity fields.
+With the given parameters  $L, M, \xi, P, m$, we have that the two error has the bound:
+\begin{align}
+E^F & \le C_F e^{-\frac{M^2 \pi^2}{4 L \xi^2}}, \quad C_F \approx 1 \\
+E^Q & \le  4 e^{- \frac{\pi^2 P^2}{2 m^2 L^2}} + \text{erfc} (m / \sqrt{2})
+\end{align}
+For the real space, the truncation error has the bound
+\begin{equation}
+E^R \le C_R (\xi + \frac{p_{\infty}}{\xi}) e^{-p_{\infty}^2 \xi^2}, \quad C_R \approx 0.1.
+\end{equation}
 \end{document}

### 2019-05-21 report/slides.tex

\documentclass{beamer}
\mode<presentation> {\usetheme{Frankfurt}}

\usepackage{graphicx} % Allows including images
\usepackage{amsmath,amsthm,amsfonts,graphicx,bm,bbm,wrapfig}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{color}
\usepackage{breqn}
\usepackage{subfigure}
\usepackage{float}
\usepackage{color}

\title[HPC Final Project]{HPC final project: \\
	Ewald summation on stokes potential} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{Zhe Chen, Guanchun Li} % Your name
\institute[CIMS] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Courant Insititute of Mathematical sciences \\ % Your institution for the title page
\medskip
\textit{gl1705@nyu.edu} % Your email address
}
\date{\today} % Date, can be changed to a custom date

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\section{Background of Ewald Summation}
\begin{frame}{Periodic Stokes potentials}
Consider a system of $N$ point sources at location $\mathbf{x}_n$ with strength $\mathbf{f}_n$, in the periodic setting, the velocity field is 
\begin{equation}
\mathbf{u}(\mathbf{x}) = \sum_{n=1}^{N} \sum_{\mathbf{p}} \mathbf{S}(\mathbf{x - x_n + p}) \mathbf{f}_n, \label{eq:stokes_velocity_field}
\end{equation} 
with $\mathbf{S}$ the Oseen-Burgers tensor:
\begin{equation}
\mathbf{S}(\mathbf{x}) = \frac{\mathbf{1}}{|\mathbf{x}|} + \frac{\mathbf{x x}}{|\mathbf{x}|^3}.
\end{equation}

where $\mathbf{p}$ form the discrete set $\{[iL_x \ jL_y \  kL_z]:(i, j, k) \in \mathbb{Z}^3\}$.\\

\textbf{Warning: Eq.\eqref{eq:stokes_velocity_field} decays as $1 / |\mathbf{x}|$!} \\

We need \textbf{Ewald summation} to compute this.
\end{frame}

\begin{frame}{Ewald summation}
\begin{eqnarray}
\mathbf{u}(\mathbf{x}_m) = &  \sum_{n=1}^{N} \sum_{\mathbf{p}} \mathbf{A}(\xi, \mathbf{x_m - x_n + p}) \mathbf{f}_n  - \mathbf{u}_{\text{self}} \label{eq:ewald_sum} \notag \\ 
+ &  \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) e^{-k^2/4\xi^2}\sum_{n=1}^{N} \mathbf{f}_n e ^{-i \mathbf{k} \cdot (\mathbf{x}_m - \mathbf{x}_n)} 
\end{eqnarray}

By the formulation by Hasimoto \cite{Hasimoto1959}, we have
\begin{eqnarray}
& \mathbf{A}(\xi, \mathbf{x}) = 2 \left(\frac{\xi e^{-\xi^2 r^2}}{\sqrt{\pi} r^2} + \frac{\text{erfc}(\xi r)}{2 r^3}\right) (r^2 \mathbf{I} + \mathbf{x x}) - \frac{4 \xi}{\sqrt{\pi}} e^{-\xi^2 r^2} \mathbf{I} \\
& B(\xi, \mathbf{k}) = 8 \pi \left(1 + \frac{k^2}{4 \xi^2}\right) \frac{1}{k^4}(k^2 \mathbf{I} - \mathbf{k k})\\
& \mathbf{u}_{\text{self}}(\mathbf{x}_m) = \frac{4 \xi}{\sqrt{\pi}} \mathbf{f}_m
\end{eqnarray}
$\xi$ is a positive constant known as the \textbf{Ewald parameter}.
\end{frame}

\section{Description of Algorithms}

\begin{frame}{Compute $u^F$ by FFT}
\begin{equation}
\mathbf{u}^F (\mathbf{x}_m) = \frac{1}{V} \sum_{\mathbf{k} \neq 0} \mathbf{B}(\xi, \mathbf{k}) e^{-k^2/4\xi^2} \left(\sum_{n=1}^{N} \mathbf{f}_n e ^{i \mathbf{k} \cdot \mathbf{x}_n} \right)e ^{-i \mathbf{k} \cdot \mathbf{x}_m}
\end{equation}
is the combination of two steps of NuFFT (Non-uniform FFT).

\textbf{Can be done efficiently by Gaussian Gridding \& FFT!}
\begin{itemize}
	\item \textbf{Gaussian Gridding}: \\
	Compute $ \sum_{n=1}^N \mathbf{f}_n e^{-2 \xi^2 |\mathbf{x} - \mathbf{x}_n|_{\ast}^2 / \eta}$ \\
	Can be accelerated with Greengard's trick \cite{Greengard2004} and  OpenMP!
	\item \textbf{FFT}: \\
	Can be done efficiently by CuFFT (GPU) / FFTW (CPU) !
\end{itemize}
\end{frame}

\begin{frame}{Important Parameters \& Error bound}
Free parameters:
\begin{itemize}
	\item $\xi$ : Ewald parameter
	\item $M$: Number of layers of k-space
	\item $p_{\infty}$: Number of layers of real-space
	\item $P, m$: control the error of truncated Gaussian function
\end{itemize}
Error Bound: \textbf{Spectral accurate!}
\begin{align}
E & = E^F + E^Q + E^R \\
E^F & \le C_F e^{-\frac{M^2 \pi^2}{4 L \xi^2}} \quad  \text{(truncation of k-space)}\\
E^Q & \le  4 e^{- \frac{\pi^2 P^2}{2 m^2 L^2}} + \text{erfc} (m / \sqrt{2}) \quad  \text{(quadrature)}\\
E^R & \le C_R (\frac{1}{\xi^2} + \frac{p_{\infty}}{\xi}) e^{-p_{\infty}^2 \xi^2}. \quad \text{(truncation of real space)}
\end{align}
\textbf{Ewald parameter $\xi$ trades off between real space and k-space!}
\end{frame}

\section{Implementation \& results}
\begin{frame}{Time Complexity \& Work load balance}
The total computational cost of the method is
\begin{equation}
\underbrace{O(NP^3)}_{\text{Gaussian gridding}} + \underbrace{O(M^3 \log(M^3))}_{\text{FFT + iFFT}} + \underbrace{O(M^3)}_{\text{Scaling on k-space}} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}}
\end{equation}
\textbf{Ewald parameter $\xi$ trades off between real space and k-space!}
\begin{itemize}
	\item Larger $\xi \rightarrow$ larger $M$, smaller $p_{\infty}$.
	\item Smaller $\xi \rightarrow$ smaller $M$, larger $p_{\infty}$.
\end{itemize}
How we choose the parameters:
\begin{itemize}
	\item \textbf{Balance the error} \\
	\item \textbf{Balance the time}
\end{itemize}
\end{frame}

\begin{frame}{Scalability result}
content...
\end{frame}
\section{Acknowledgments}

\begin{frame}{References}
	\begin{thebibliography}{0}
		\bibitem{Greengard2004}
		Greengard, Leslie, and June-Yub Lee. "Accelerating the nonuniform fast Fourier transform." SIAM review 46.3 (2004): 443-454.
		\bibitem{Hasimoto1959}
		Hasimoto, Hidenori. "On the periodic fundamental solutions of the Stokes equations and their application to viscous flow past a cubic array of spheres." Journal of Fluid Mechanics 5.2 (1959): 317-328.
	\end{thebibliography}
\end{frame}

\end{document}

### 2019-05-21 report/slides.tex
Update the slides

@@
 
-\begin{frame}{Compute $u^F$ by FFT}
+\begin{frame}{Acceleration \& parallelization}
+\begin{itemize}
+	\item Compute $u^F$ (k-space) by FFT \\
 	\begin{equation}
@@
 	\end{itemize}
+
+	\item Accelerate $u^R$ (real space) by OpenMP 
+\end{itemize}
+
 \end{frame}
@@
 \section{Implementation \& results}
+
+\begin{frame}{Spectral convergence}
+The three type of error versus the corresponding parameter, \\
+all has \textbf{spectral convergence}!
+\begin{figure}[H]\centering
+	\includegraphics[width=.36\textwidth]{freq_error_vs_k}
+	\includegraphics[width=.36\textwidth]{qudrature_error_vs_P}
+	\includegraphics[width=.36\textwidth]{real_error_vs_r}
+\end{figure}
+\end{frame}
 \begin{frame}{Time Complexity \& Work load balance}
@@
 \begin{equation}
-\underbrace{O(NP^3)}_{\text{Gaussian gridding}} + \underbrace{O(M^3 \log(M^3))}_{\text{FFT + iFFT}} + \underbrace{O(M^3)}_{\text{Scaling on k-space}} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}}
+\underbrace{O(NP^3)}_{\text{Gaussian gridding}} + \underbrace{O(M^3 \log(M^3))}_{\text{FFT + iFFT}} + \underbrace{O(M^3)}_{\text{Scaling on k-space}} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}} + \underbrace{O(N)}_{self}
+\end{equation}
+if no FFT acceleration, the cost is
+\begin{equation}
+\underbrace{O(N^2M^3)}_{k-space} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}} + \underbrace{O(N)}_{self}
 \end{equation}

### 2019-05-21 src/ewald.cu
fftw

@@ -9,6 +9,7 @@
 #include <stdlib.h>
 #include <omp.h>
 #include <chrono>
+#include "fftw3.h"
 #include "ewald.h"
 #include "utils.h"
 
@@ -462,7 +463,7 @@ void Gaussian_Gridding_type2(double* H){
   return;
 }
 
-void FFT3D(double *H, complex<double> *odata){
+void FFT3DGPU(double *H, complex<double> *odata){
   cufftHandle plan;
   cufftDoubleReal *data;
   cufftDoubleComplex *data1;
@@ -504,7 +505,7 @@ void FFT3D(double *H, complex<double> *odata){
   printf("FFT finished with %f(s)\n",(tt.toc()));
   return;
 }
-void IFFT3D(complex<double> *H, double *odata){
+void IFFT3DGPU(complex<double> *H, double *odata){
   cufftHandle plan;
   cufftDoubleReal *data;
   cufftDoubleComplex *data1;
@@ -553,6 +554,70 @@ void IFFT3D(complex<double> *H, double *odata){
   return;
 }
 
+void FFT3D(double *H, complex<double> *odata){
+  fftw_complex *out;
+  double *in;
+  fftw_plan p;
+  Timer tt;
+  tt.tic();
+  out = (fftw_complex*) fftw_malloc(sizeof(fftw_complex) * nx*ny*(nz/2+1));
+  in = (double*) fftw_malloc(sizeof(double) * nx*ny*(nz));
+  p = fftw_plan_dft_r2c_3d(nx, ny, nz, in, out, FFTW_ESTIMATE);
+
+  memcpy(in, &(H[0*nx*ny*(nz)]), sizeof(double)*nx*ny*(nz));
+  fftw_execute(p); /* repeat as needed */
+  memcpy(&(odata[0*nx*ny*(nz/2+1)]), out, sizeof(complex<double>)*nx*ny*(nz/2+1));
+
+  memcpy(in, &(H[1*nx*ny*(nz)]), sizeof(double)*nx*ny*(nz));
+  fftw_execute(p); /* repeat as needed */
+  memcpy(&(odata[1*nx*ny*(nz/2+1)]), out, sizeof(complex<double>)*nx*ny*(nz/2+1));
+
[…]

### 2019-05-21 src/fftw3.h

@@ -1,0 +1,410 @@
+/*
+ * Copyright (c) 2003, 2007-11 Matteo Frigo
+ * Copyright (c) 2003, 2007-11 Massachusetts Institute of Technology
+ *
+ * The following statement of license applies *only* to this header file,
+ * and *not* to the other files distributed with FFTW or derived therefrom:
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ *
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS
+ * OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED
+ * WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ * ARE DISCLAIMED. IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR ANY
+ * DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
+ * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE
+ * GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY,
+ * WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
+ * NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
+ * SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ */
+
+/***************************** NOTE TO USERS *********************************
+ *
+ *                 THIS IS A HEADER FILE, NOT A MANUAL
+ *
+ *    If you want to know how to use FFTW, please read the manual,
+ *    online at http://www.fftw.org/doc/ and also included with FFTW.
+ *    For a quick start, see the manual's tutorial section.
+ *
[…]

### 2019-05-21 src/ewald.cu
Add reading parameters from cmd

@@ -50,6 +50,40 @@ void initialize(){
 }
 
 
+void initialize_readinput(int N, int num_p, int P, double eta_in, 
+  int rp, double L, double xi_in){
+  srand((unsigned int) 100005);
+  nx = N;
+  ny = N;
+  nz = N;
+  Lx = L;
+  Ly = L;
+  Lz = L;
+  eta = eta_in;
+  xi = xi_in;
+  np = num_p;
+  px = P;
+  py = P;
+  pz = P;
+  repeat_x = rp;
+  repeat_y = rp;
+  repeat_z = rp;
+  grid = (double*)calloc(np*DIM,sizeof(double));
+  particle = (double*)calloc(np*DIM,sizeof(double));
+  strength = (double*)calloc(np*DIM,sizeof(double));
+  vel = (double*)calloc(np*DIM,sizeof(double));
+  for (int i = 0; i<np; i++){
+    particle[DIM*i+0] = rand()*1.0/RAND_MAX*Lx;
+    particle[DIM*i+1] = rand()*1.0/RAND_MAX*Ly;
+    particle[DIM*i+2] = rand()*1.0/RAND_MAX*Lz;
+    strength[DIM*i+0] = 1.0;
+    strength[DIM*i+1] = 1.0;
+    strength[DIM*i+2] = 1.0;
+  }
+  outputfile = "../results/vel2.txt";
+  cout << "System initialized! # of particles: " << np << '\n';
+}
+
 void realfunc(double x, double y, double z, double xi, double *st1, double *st2, double *v){
   double r2 = x*x + y*y + z*z;
   double r = sqrt(r2);

### 2019-05-21 src/ewald.h

@@ -5,6 +5,8 @@ using namespace std;
 
 
 void initialize();
+void initialize_readinput(int N, int num_p, int P, double eta_in, 
+  int rp, double L, double xi_in);
 void realspace();
 void realspaceOMP(int num_threads);
 void kspace();

### 2019-05-21 src/main.cpp
Modify main.cpp \& add the report & numerical result

@@ -12,11 +12,26 @@ using namespace std;
 // nvcc -std=c++11 -O3   main.cpp ewald.cu global.cpp -lcufft -o ewald
 int main(int argc, char* argv[]){
   int num_threads = 1;
-  cout << "Please input num of threads(default=1): " << endl;
-	cin >> num_threads;
+  // cout << "Please input num of threads(default=1): " << endl;
+	// cin >> num_threads;
+  sscanf(argv[1], "%d", &num_threads); 
+  int N, num_p, P, rp;
+  double L = 2.0, xi_in = 12.0, eta_in = 1.15;  
+  sscanf(argv[2], "%d", &N);
+  sscanf(argv[3], "%d", &num_p);
+  // sscanf(argv[3], "%f", &xi_in);
+  // sscanf(argv[4], "%f", &eta_in);
+  sscanf(argv[4], "%d", &P);
+  sscanf(argv[5], "%d", &rp);
+  // sscanf(argv[7], "%f", &L);  
+  printf("Size N = %d with %d particles \n", N, num_p);
+  printf("Gaussian P = %d, Real layer rp = %d \n", P, rp);
+  printf("Length L = %f, xi = %f, eta = %f", L, xi_in, eta_in);
+
   long tt = clock();
   cout << "\n---------------initialize---------------" << endl;
-  initialize();
+  // initialize();
+  initialize_readinput(N, num_p, P, eta_in, rp, L, xi_in);
   cout << "\n---------------Real Space---------------" << endl;
   realspace();
   cout << "\n---------------Real Space OMP---------------" << endl;

### 2019-05-26 report/draft.tex
Change the tex file of report

@@
 where $|\cdot|_{\ast}$ denotes distance to closest periodic image.
-(\textit{Remark from Guanchun: The distance is a little weird, I haven't checked if it's the Fourier transform or not.
-Is it common in periodic setting?})
 
@@
 
-\paragraph{Fast Gaussian Gridding} The idea of fast Gaussian gridding is pre-compute and store the exponential and only do necessary multiplications.
+\paragraph{Truncation error of Gaussian Gridding}
+Since the Gaussian function has the infinite support, we have to truncate the Gaussian function to get the numerical value.
+Denote the grid size of real space (in one dimension) is $h$ and number of grids in the support of truncated Gaussian as $P$, then the value of Gaussian at the truncated points is $e^{- \xi^2 P^2 h^2 / 2 \eta}$.
+Let
+\begin{equation}
+\eta =  \left(\frac{P h \xi}{m} \right)^2 \label{eq:eta_formula}
+\end{equation}
+we know the Gaussian at the truncated points is $e^{-m^2/2}$.
 
-Roughly speaking, for 1D situation, we have that ($x_{(i)} = ih$)
+Moreover, we can bound the quadrature error from  Eq.\eqref{eq:gaussian_gridding_1} and Eq.\eqref{eq:gaussian_gridding_2} by
 \begin{equation}
-e^{-\alpha|x_{(i)} - x_n|^2} = e^{-\alpha|ih - x_n|^2} = e^{-\alpha (ih)^2} \left(e^{2 \alpha h x_n}\right)^i e^{-\alpha x_n^2}
+E^Q \le  4 e^{- \frac{\pi^2 P^2}{2 m^2 L^2}} + \text{erfc} (m / \sqrt{2}).
 \end{equation}
-All $e^{-\alpha (ih)^2}, e^{2 \alpha h x_n}, e^{-\alpha x_n^2}$ can be precomputed and then each time we only need to do some multiplications.
+\textbf{Note that by choosing the free parameter $\eta$ as Eq.\eqref{eq:eta_formula}, we can decouple the quadrature error with the Ewald parameter $\xi$, which makes it easier to determine the parameters.}
 
-\textit{Remark from Guanchun: It's said to be 5 to 10 times faster in 2D than naive method and will perform better in higher dimension.
-However, I was wondering if we do the naive matrix multiplication on GPU, maybe it's still fast enough?}
+\paragraph{Fast Gaussian Gridding and Parallelization} Denote $N$ as the number of particles and $M$ the number of layers in k-space, then if we compute Eq.\eqref{eq:gaussian_gridding_1} and Eq.\eqref{eq:gaussian_gridding_2} directly, the computation cost (each) is $NM^3$ exponential computation, $3NM^3$ multiplications and additions.
+Since exponential takes much more time than multiplication ($15 \sim 20$ time clocks than $1 \sim 2$ time clocks), a natural idea is to substitute exponential operation with multiplication.
+\textbf{The idea of fast Gaussian gridding is to pre-compute and store the exponential and only do necessary multiplications afterwards.}
+
+Roughly speaking, take 1D situation for example, we have that ($x_{(i)} = ih, x_n = \tilde{x}_n + jh, 0 \le \tilde{x}_n < h$)
+\begin{equation}
+e^{-\alpha|x_{(i)} - x_n|^2} = e^{-\alpha|ih - jh - \tilde{x}_n|^2} = e^{-\alpha ((i-j)h)^2} \left(e^{2 \alpha h \tilde{x}_n}\right)^i e^{-\alpha \tilde{x}_n^2}
+\end{equation}
+All $e^{-\alpha ((i-j)h)^2}, e^{2 \alpha h \tilde{x}_n}, e^{-\alpha \tilde{x}_n^2}$ can be precomputed with only $\mathbf{2(M+N)}$ exponential computations (also that much storage cost) and then we only need to do $2 NM$ more multiplications to get all $e^{-\alpha|x_{(i)} - x_n|^2}$.
+For 3D situation we need $\mathbf{6(M+N)}$ exponential computations and $2 NM^3$ more multiplications.
+\textbf{As long as the exponential takes significantly more time than multiplication, the fast Gaussian gridding will improve the performance and it will benefit more with higher dimension.}
+
+As for the parallelization, the parallelization of Eq.\eqref{eq:gaussian_gridding_2} is simple since we can compute the velocity filed $\mathbf{u}^F (\mathbf{x}_m)$ at each point source $\mathbf{x}_m$ separately , thus parallelly.
+Since usually we have a large number of source points and there's no communication between threads, it's a parallelization with high-efficiency.
+
+However, the parallelization of Eq.\eqref{eq:gaussian_gridding_1} is not that ideal since (almost) every source point contributes to the grid points and it will need great memory cost if we still parallelize on the source points.
+Thus \textit{instead we parallelize on the grid points to avoid the repeating IO for grid points.} To be more specific, for each source point we parallelize on the grid points that will be affected by the source (since we use a truncated Gaussian) and do the computation serially on the source points.
+We will see later it's not as efficient as the parallelization of Eq.\eqref{eq:gaussian_gridding_2}, but it did reduce the computation time with more cores.
 
@@
 \paragraph{Error estimation}
-For k-space, the error comes from two parts: the truncation error in the k-space and the quadrature error to get the velocity fields.
+\begin{align}
+E & = E^F + E^Q + E^R \\
+E^F & \le C_F e^{-\frac{M^2 \pi^2}{4 L \xi^2}} \quad  \text{(truncation of k-space)}\\
+E^R & \le C_R (\frac{1}{\xi^2} + \frac{p_{\infty}}{\xi}) e^{-p_{\infty}^2 \xi^2}. \quad \text{(truncation of real space)} \\
+E^Q & \le  4 e^{- \frac{\pi^2 P^2}{2 m^2 L^2}} + \text{erfc} (m / \sqrt{2}) \quad  \text{(quadrature)}
+\end{align}
+For k-space, the error comes from two parts: the truncation error in the k-space $E^F$ and the quadrature error $E^Q$ to get the velocity fields.
 With the given parameters  $L, M, \xi, P, m$, we have that the two error has the bound:
@@
 \end{equation}
+We can see that all three parts of error decay exponentially with the corresponding parameter $E^F$ with $M$, $E^Q$ with $P$ and $E^R$ with $p_{\infty}$). It's also been shown numerically.
+
+\paragraph{Time complexity and speed up}
+The total computational cost of the method is
+\begin{equation}
+\underbrace{O(NP^3)}_{\text{Gaussian gridding}} + \underbrace{O(M^3 \log(M^3))}_{\text{FFT + iFFT}} + \underbrace{O(M^3)}_{\text{Scaling on k-space}} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}} + \underbrace{O(N)}_{self}
+\end{equation}
+if no FFT acceleration, the cost is
+\begin{equation}
+\underbrace{O(N^2M^3)}_{k-space} + \underbrace{O(N^2 p_{\infty}^3)}_{\text{Real space}} + \underbrace{O(N)}_{self}
+\end{equation}
+\textbf{Ewald parameter $\xi$ trades off between real space and k-space!}
+\begin{itemize}
+	\item Larger $\xi \rightarrow$ larger $M$, smaller $p_{\infty}$.
+	\item Smaller $\xi \rightarrow$ smaller $M$, larger $p_{\infty}$.
+\end{itemize}
+How we choose the parameters:
+\begin{itemize}
+	\item \textbf{Balance the error} \\
+	\item \textbf{Balance the time}
+\end{itemize}
+
+\paragraph{Weak scaling result}
+
+\paragraph{Strong scaling result}
+
+\paragraph{Information about the project} 
+Link of the project:
+
+\url{https://github.com/CecilMartin/Ewald_Summation}
+
+Team work:
+\begin{itemize}
+	\item Zhe Chen: Write codes, presentation
+	\item Guanchun Li:  Develop algorithm into pseudo-code, run codes, write slides
+	\item Together: Literature research
+\end{itemize}
+
+\begin{thebibliography}{0}
+	\bibitem{Greengard2004}
+	Greengard, Leslie, and June-Yub Lee. "Accelerating the nonuniform fast Fourier transform." SIAM review 46.3 (2004): 443-454.
+	\bibitem{Hasimoto1959}
+	Hasimoto, Hidenori.
+"On the periodic fundamental solutions of the Stokes equations and their application to viscous flow past a cubic array of spheres." Journal of Fluid Mechanics 5.2 (1959): 317-328.
+	\bibitem{Lindbo2010}
+	Lindbo, Dag, and Anna-Karin Tornberg. "Spectrally accurate fast summation for periodic Stokes potentials." Journal of Computational Physics 229.23 (2010): 8994-9010.
+	\bibitem{FFTW3}
+	Frigo, Matteo, and Steven G. Johnson. "The design and implementation of FFTW3." Proceedings of the IEEE 93.2 (2005): 216-231.
+	\bibitem{cufft}
+	\url{https://developer.nvidia.com/cufft}
+	\bibitem{openmp}
+	Dagum, Leonardo, and Ramesh Menon. "OpenMP: An industry-standard API for shared-memory programming." Computing in Science \& Engineering 1 (1998): 46-55.
+\end{thebibliography}
+
 \end{document}

### 2019-05-26 src/matlab/error_estimate.m
matlab initialize

@@ -1,0 +1,22 @@
+L = 2;
+M = 54;
+xi = 12;
+m = 8;
+P = 24;
+pr = 2;
+np = 1024;
+
+
+C_F = 1; C_R = 50; 
+eta = (P*L*xi / (M*m))^2;
+E_F = C_F * exp(-pi^2 * M^2 / (4*L*xi^2));
+E_Q = 4 * exp(-pi^2 * P^2 / (2*m^2)) + erfc(m / sqrt(2));
+E_R = C_R * (1 / (xi^2) + pr / xi) * exp(-pr^2 * xi^2);
+
+C_tR = 5e-7; C_tF = 7e-9; C_tG = 1e-7;
+t_R = C_tR * np^2 * pr^3;
+t_F = C_tF * (M^3) * log(M^3);
+t_G = 2 * C_tG * np * P^3;
+time = t_R + t_F + t_G + 0.5;
+fprintf(['eta = ', num2str(eta), ' E_F = ', num2str(E_F), ' E_Q = ', num2str(E_Q), ' E_R = ', num2str(E_R), ' \n']);
+fprintf(['time = ', num2str(time), ' t_F = ', num2str(t_F), ' t_G = ', num2str(t_G), ' t_R = ', num2str(t_R), ' \n']);

### 2019-05-26 src/error_estimate.m
merged

@@ -1,22 +1,0 @@
-L = 2;
-M = 54;
-xi = 4;
-m = 8;
-P = 24;
-pr = 2;
-np = 1024;
-
-
-C_F = 1; C_R = 50; 
-eta = (P*L*xi / (M*m))^2;
-E_F = C_F * exp(-pi^2 * M^2 / (4*L*xi^2));
-E_Q = 4 * exp(-pi^2 * P^2 / (2*m^2)) + erfc(m / sqrt(2));
-E_R = C_R * (1 / (xi^2) + pr / xi) * exp(-pr^2 * xi^2);
-
-C_tR = 5e-7; C_tF = 7e-9; C_tG = 1e-7;
-t_R = C_tR * np^2 * pr^3;
-t_F = C_tF * (M^3) * log(M^3);
-t_G = 2 * C_tG * np * P^3;
-time = t_R + t_F + t_G + 0.5;
-fprintf(['eta = ', num2str(eta), ' E_F = ', num2str(E_F), ' E_Q = ', num2str(E_Q), ' E_R = ', num2str(E_R), ' \n']);
-fprintf(['time = ', num2str(time), ' t_F = ', num2str(t_F), ' t_G = ', num2str(t_G), ' t_R = ', num2str(t_R), ' \n']);

### 2019-05-26 report/draft.tex
Update the tex

@@
 \paragraph{Reformulation by Gaussian Gridding \& FFT} 
-The basic idea is convolution by the Gaussian... leave it for later.
+The basic idea of conducting NuFFT here is to consider the point source as delta function and convolve it with Gaussian function to smooth it in the real space, which makes it possible to the uniform FFT.
+Then we conduct deconvolution in the frequency space by scaling (element-wise multiplication) and get the finally result.
+We will give more details in this section.
 

### 2019-05-26 src/matlab/error_estimate.m
Modify error_estimate.m
Fix the expression for k-space error

@@ -1,6 +1,6 @@
 L = 2;
-M = 54;
-xi = 12;
+M = 53;
+xi = 10;
 m = 8;
 P = 24;
 pr = 2;
@@ -9,7 +9,7 @@ np = 1024;
 
 C_F = 1; C_R = 50; 
 eta = (P*L*xi / (M*m))^2;
-E_F = C_F * exp(-pi^2 * M^2 / (4*L*xi^2));
+E_F = C_F * exp(-pi^2 * M^2 / (4*L^2*xi^2));
 E_Q = 4 * exp(-pi^2 * P^2 / (2*m^2)) + erfc(m / sqrt(2));
 E_R = C_R * (1 / (xi^2) + pr / xi) * exp(-pr^2 * xi^2);
 

### 2019-05-27 src/conv/ewald.cu
convergence test

@@ -1,0 +1,853 @@
+#include <cmath>
+#include <vector>
+#include <ctime>
+#include <fstream>
+#include <iostream>
+#include <complex>
+#include <cufft.h>
+#include <cstdio>
+#include <stdlib.h>
+#include <omp.h>
+#include <chrono>
+#include "fftw3.h"
+#include "ewald.h"
+#include "utils.h"
+
+using namespace std;
+using namespace chrono;
+
+void writeoutpart(double *vel, string outputfile);
+
+void initialize(){
+  srand((unsigned int) 100005);
+  nx = 64;
+  ny = 64;
+  nz = 64;
+  Lx = 2.0;
+  Ly = 2.0;
+  Lz = 2.0;
+  eta = 1.15;
+  xi = 12;
+  np = 2048;
+  px = 24;
+  py = 24;
+  pz = 24;
+  repeat_x = 2;
+  repeat_y = 2;
+  repeat_z = 2;
+  grid = (double*)calloc(np*DIM,sizeof(double));
+  particle = (double*)calloc(np*DIM,sizeof(double));
+  strength = (double*)calloc(np*DIM,sizeof(double));
+  vel = (double*)calloc(np*DIM,sizeof(double));
+  for (int i = 0; i<np; i++){
+    particle[DIM*i+0] = rand()*1.0/RAND_MAX*Lx;
+    particle[DIM*i+1] = rand()*1.0/RAND_MAX*Ly;
+    particle[DIM*i+2] = rand()*1.0/RAND_MAX*Lz;
+    strength[DIM*i+0] = 1.0;
+    strength[DIM*i+1] = 1.0;
+    strength[DIM*i+2] = 1.0;
+  }
+  outputfile = "../results/vel2.txt";
+  cout << "System initialized! # of particles: " << np << '\n';
+}
+
+
+void initialize_readinput(int N, int num_p, int P, double eta_in, int rp, double L, double xi_in){
+  srand((unsigned int) 100005);  
+  // srand((unsigned int) clock());
+  nx = N;
+  ny = N;
+  nz = N;
+  Lx = L;
+  Ly = L;
+  Lz = L;
+  eta = eta_in;
+  xi = xi_in;
+  np = num_p;
+  px = P;
+  py = P;
+  pz = P;
+  repeat_x = rp;
+  repeat_y = rp;
+  repeat_z = rp;
[…]

### 2019-05-27 src/conv/ewald.h

@@ -1,0 +1,25 @@
+#ifndef EWALD_H
+#define EWALD_H
+#define DIM 3
+using namespace std;
+
+
+void initialize();
+void initialize_readinput(int N, int num_p, int P, double eta_in, 
+  int rp, double L, double xi_in);
+void realspace();
+void realspaceOMP(int num_threads);
+void kspace();
+void kspaceParallel();
+void selfcontribution();
+void writeout();
+void free();
+
+extern int nx, ny, nz, np, px, py, pz, repeat_x, repeat_y, repeat_z;
+extern double Lx, Ly, Lz, xi, eta;
+
+extern double *grid, *particle, *strength, *vel;
+
+extern string outputfile;
+
+#endif

### 2019-05-27 src/conv/main.cpp

@@ -1,0 +1,49 @@
+#include <cmath>
+#include <vector>
+#include <ctime>
+#include <cstdio>
+#include <string>
+#include <iostream>
+#include "ewald.h"
+
+using namespace std;
+
+// nvcc -std=c++11 -O0 -g  main.cpp ewald.cu global.cpp -lcufft -o ewald
+// nvcc -std=c++11 -O3   main.cpp ewald.cu global.cpp -lcufft -o ewald
+int main(int argc, char* argv[]){
+  int num_threads = 1;
+  // cout << "Please input num of threads(default=1): " << endl;
+	// cin >> num_threads;
+  sscanf(argv[1], "%d", &num_threads);
+  int N, num_p, P, rp;
+  double L = 1.0, xi_in = 0.2, eta_in = 0.025;
+  sscanf(argv[2], "%d", &N);
+  sscanf(argv[3], "%d", &num_p);
+  // sscanf(argv[3], "%f", &xi_in);
+  // sscanf(argv[4], "%f", &eta_in);
+  sscanf(argv[4], "%d", &P);
+  sscanf(argv[5], "%d", &rp);
+  // sscanf(argv[7], "%f", &L);
+  printf("Size N = %d with %d particles \n", N, num_p);
+  printf("Gaussian P = %d, Real layer rp = %d \n", P, rp);
+  printf("Length L = %f, xi = %f, eta = %f", L, xi_in, eta_in);
+
+  long tt = clock();
+  cout << "\n---------------initialize---------------" << endl;
+  // initialize();
+  initialize_readinput(N, num_p, P, eta_in, rp, L, xi_in);
+  // cout << "\n---------------Real Space---------------" << endl;
+  // realspace();
+  cout << "\n---------------Real Space OMP---------------" << endl;
+  realspaceOMP(num_threads);
+  // cout << "\n---------------K-Space---------------" << endl;
+  // kspace();
+  cout << "\n---------------K-Space Parallel---------------" << endl;
+  kspaceParallel();
+  cout << "\n---------------Self Contribution---------------" << endl;
+  selfcontribution();
+  writeout();
+  cout << "\n---------------In Total---------------" << endl;
+  printf("Total time is %f(s)\n",(clock()-tt)*1.0/CLOCKS_PER_SEC);
+  return 0;
+}

### 2019-05-27 src/matlab/error_estimate.m

@@ -1,17 +1,17 @@
-L = 2;
-M = 53;
-xi = 10;
-m = 8;
-P = 24;
-pr = 2;
-np = 1024;
+L = 1;
+M = 5; %nx
+xi = 2;
+m = 8; %std of sigma of gaussian kernel
+P = M; %points within support of Gaussian kernel
+pr = 0; % layers of real space
+np = 100; % # of points
 
-
+fprintf('------------------------------------------------------------\n')
 C_F = 1; C_R = 50; 
 eta = (P*L*xi / (M*m))^2;
-E_F = C_F * exp(-pi^2 * M^2 / (4*L^2*xi^2));
-E_Q = 4 * exp(-pi^2 * P^2 / (2*m^2)) + erfc(m / sqrt(2));
-E_R = C_R * (1 / (xi^2) + pr / xi) * exp(-pr^2 * xi^2);
+E_F = C_F * exp(-pi^2 * M^2 / (4*L^2*xi^2)); % k-space // nx (14)
+E_Q = 4 * exp(-pi^2 * P^2 / (2*m^2)) + erfc(m / sqrt(2)); % quadrature error // P (25)
+E_R = C_R * (1 / (xi^2) + pr / xi) * exp(-pr^2 * xi^2); % real space (16)
 
 C_tR = 5e-7; C_tF = 7e-9; C_tG = 1e-7;
 t_R = C_tR * np^2 * pr^3;

### 2019-05-27 src/matlab/main.m

@@ -1,0 +1,74 @@
+%Zhe Chen
+%Script to run ewald summation and check convergence
+%%
+L = 1;
+M = 5; %nx
+xi = 0.5;
+m = 8; %std of sigma of gaussian kernel
+P = M; %points within support of Gaussian kernel
+pr = 1; % layers of real space
+np = 100; % # of points
+fprintf('------------------------------------------------------------\n')
+C_F = 1; C_R = 50; 
+eta = (P*L*xi / (M*m))^2;
+E_F = C_F * exp(-pi^2 * M^2 / (4*L^2*xi^2)); % k-space // nx (14)
+E_Q = 4 * exp(-pi^2 * P^2 / (2*m^2)) + erfc(m / sqrt(2)); % quadrature error // P (25)
+E_R = C_R * (1 / (xi^2) + pr / xi) * exp(-pr^2 * xi^2); % real space (16)
+
+C_tR = 5e-7; C_tF = 7e-9; C_tG = 1e-7;
+t_R = C_tR * np^2 * pr^3;
+t_F = C_tF * (M^3) * log(M^3);
+t_G = 2 * C_tG * np * P^3;
+time = t_R + t_F + t_G + 0.5;
+fprintf(['eta = ', num2str(eta), ' E_F = ', num2str(E_F), ' E_Q = ', num2str(E_Q), ' E_R = ', num2str(E_R), ' \n']);fprintf('------------------------------------------------------------\n')
+C_F = 1; C_R = 50; 
+eta = (P*L*xi / (M*m))^2;
+E_F = C_F * exp(-pi^2 * M^2 / (4*L^2*xi^2)); % k-space // nx (14)
+E_Q = 4 * exp(-pi^2 * P^2 / (2*m^2)) + erfc(m / sqrt(2)); % quadrature error // P (25)
+E_R = C_R * (1 / (xi^2) + pr / xi) * exp(-pr^2 * xi^2); % real space (16)
+
+C_tR = 5e-7; C_tF = 7e-9; C_tG = 1e-7;
+t_R = C_tR * np^2 * pr^3;
+t_F = C_tF * (M^3) * log(M^3);
+t_G = 2 * C_tG * np * P^3;
+time = t_R + t_F + t_G + 0.5;
+fprintf(['eta = ', num2str(eta), ' E_F = ', num2str(E_F), ' E_Q = ', num2str(E_Q), ' E_R = ', num2str(E_R), ' \n']);
+
+%%
+%real space
+clc
[…]

### 2019-05-27 src/matlab/read_ewald.m

@@ -1,0 +1,3 @@
+function data=read_ewald(filename)
+data=textread(filename,'','headerlines',2,'delimiter'," ");
+end

### 2019-05-28 src/conv/ewald.cu
convergence

@@ -9,6 +9,7 @@
 #include <stdlib.h>
 #include <omp.h>
 #include <chrono>
+#include <iomanip>
 #include "fftw3.h"
 #include "ewald.h"
 #include "utils.h"
@@ -53,7 +54,7 @@ void initialize(){
 
 
 void initialize_readinput(int N, int num_p, int P, double eta_in, int rp, double L, double xi_in){
-  srand((unsigned int) 100005);  
+  srand((unsigned int) 100005);
   // srand((unsigned int) clock());
   nx = N;
   ny = N;
@@ -821,7 +822,7 @@ void writeout(){
   output << "#Velocity obtained from Ewald summation" << endl;
   output << np << endl;
   for(long i = 0; i < np; i += 1){
-    output << i << " " << vel[DIM*i+0] << " " <<
+    output << std::setprecision(17) << i << " " << vel[DIM*i+0] << " " <<
     vel[DIM*i+1] << " " <<
     vel[DIM*i+2]<< "\n" ;
   }
@@ -835,7 +836,7 @@ void writeoutpart(double *vel, string outputfile){
   output << "#Velocity obtained from Ewald summation" << endl;
   output << np << endl;
   for(long i = 0; i < np; i += 1){
-    output << i << " " << vel[DIM*i+0] << " " <<
+    output << std::setprecision(17) << i << " " << vel[DIM*i+0] << " " <<
     vel[DIM*i+1] << " " <<
     vel[DIM*i+2]<< "\n" ;
   }

### 2019-05-28 src/conv/main.cpp

@@ -16,13 +16,18 @@ int main(int argc, char* argv[]){
 	// cin >> num_threads;
   sscanf(argv[1], "%d", &num_threads);
   int N, num_p, P, rp;
-  double L = 1.0, xi_in = 0.2, eta_in = 0.025;
+  // double L = 1.0, xi_in = 0.2, eta_in = 0.025;
+  float L, xi_in, eta_in;
   sscanf(argv[2], "%d", &N);
   sscanf(argv[3], "%d", &num_p);
   // sscanf(argv[3], "%f", &xi_in);
   // sscanf(argv[4], "%f", &eta_in);
   sscanf(argv[4], "%d", &P);
   sscanf(argv[5], "%d", &rp);
+  sscanf(argv[6], "%f", &L);
+  sscanf(argv[7], "%f", &xi_in);
+  sscanf(argv[8], "%f", &eta_in);
+
   // sscanf(argv[7], "%f", &L);
   printf("Size N = %d with %d particles \n", N, num_p);
   printf("Gaussian P = %d, Real layer rp = %d \n", P, rp);

### 2019-05-28 src/ewald.cu

@@ -9,6 +9,7 @@
 #include <stdlib.h>
 #include <omp.h>
 #include <chrono>
+#include <iomanip>
 #include "fftw3.h"
 #include "ewald.h"
 #include "utils.h"
@@ -50,7 +51,7 @@ void initialize(){
 }
 
 
-void initialize_readinput(int N, int num_p, int P, double eta_in, 
+void initialize_readinput(int N, int num_p, int P, double eta_in,
   int rp, double L, double xi_in){
   srand((unsigned int) 100005);
   nx = N;
@@ -806,7 +807,7 @@ void writeout(){
   output << "#Velocity obtained from Ewald summation" << endl;
   output << np << endl;
   for(long i = 0; i < np; i += 1){
-    output << i << " " << vel[DIM*i+0] << " " <<
+    output << std::setprecision(17) << i << " " << vel[DIM*i+0] << " " <<
     vel[DIM*i+1] << " " <<
     vel[DIM*i+2]<< "\n" ;
   }

### 2019-05-28 src/matlab/main.m

@@ -1,12 +1,15 @@
 %Zhe Chen
 %Script to run ewald summation and check convergence
 %%
+close all;
+clc;
+clear;
 L = 1;
-M = 5; %nx
-xi = 0.5;
+M = 8; %nx
+xi = 1.2;
 m = 8; %std of sigma of gaussian kernel
 P = M; %points within support of Gaussian kernel
-pr = 1; % layers of real space
+pr = 4; % layers of real space
 np = 100; % # of points
 fprintf('------------------------------------------------------------\n')
 C_F = 1; C_R = 50; 
@@ -41,34 +44,114 @@ cd ~/Cecil/Course/1st_year_spring/hpc/HPC/Ewald_Summation/src/conv
 addpath ../matlab/
 DIM=3;
 L = 1;
-M = 5; %nx
-xi = .2;
+M = 8; %nx
+% xi = 1;
+xi_all=[0.5,0.8,1];
 m = 8; %std of sigma of gaussian kernel
 P = M; %points within support of Gaussian kernel
 % pr = 1; % layers of real space
 np = 100; % # of points
 numthreads = 4;
 output="../../results/";
-pr_all=[1,2,4,8,16];
-vel_rec=cell(length(pr_all),1);
-eta=(P*L/M*xi/m)
+% pr_all=[2,4,8,16];
+pr_all=linspace(2,10,5);
+vel_rec=cell(length(pr_all),length(xi_all));
+
 for i=1:length(pr_all)
     pr=pr_all(i);
-    status = system(['./main ',num2str(numthreads),' ',num2str(M),' ',num2str(np),' ',num2str(P/2),' ',num2str(pr)],'-echo');
-    if status~=0
-        error("not successful to do ./main");
+    for j=1:length(xi_all)
+        xi=xi_all(j);
+        eta=(P*L/M*xi/m);
+        status = system(['./main ',num2str(numthreads),' ',num2str(M),' ',num2str(np),' ',num2str(P/2),' ',num2str(pr),' ',...
+            num2str(L),' ',num2str(xi),' ',num2str(eta)],'-echo');
+        if status~=0
+            error("not successful to do ./main");
+        end
+        data=read_ewald('../../results/realspace.txt');
+        vel_rec{i,j}=data(:,2:end);
     end
[…]

### 2019-05-28 src/conv/ewald.cu
Fix bugs in gaussian Gridding func
To avoid the negative integer as index

@@ -286,7 +286,7 @@ void Gaussian_Gridding_type1_OMP(double *H){
         Vy = Vx * E2_yl[j+py-1] * E3_y[abs(j)];
         for (long k = -pz+1; k <= pz; k++){
           Vz = Vy * E2_zl[k+pz-1] * E3_z[abs(k)];
-          ig = (ip+i+nx) % nx; jg = (jp+j+ny) % ny; kg = (kp+k+nz) % nz;
+          ig = (ip+i+nx*px) % nx; jg = (jp+j+ny*py) % ny; kg = (kp+k+nz*pz) % nz;
           for (long m = 0; m < DIM; m++){
             H[kg + nz*(jg + ny*(ig + m*nx))] += Vz * strength[DIM*n+m];
           }
@@ -355,7 +355,7 @@ void Gaussian_Gridding_type1(double *H){
         Vy = Vx * E2_yl[j+py-1] * E3_y[abs(j)];
         for (long k = -pz+1; k <= pz; k++){
           Vz = Vy * E2_zl[k+pz-1] * E3_z[abs(k)];
-          ig = (ip+i+nx) % nx; jg = (jp+j+ny) % ny; kg = (kp+k+nz) % nz;
+          ig = (ip+i+nx*px) % nx; jg = (jp+j+ny*py) % ny; kg = (kp+k+nz*pz) % nz;
           for (long m = 0; m < DIM; m++){
             H[kg + nz*(jg + ny*(ig + m*nx))] += Vz * strength[DIM*n+m];
           }
@@ -425,7 +425,7 @@ void Gaussian_Gridding_type2_OMP(double* H){
         Vy = Vx * E2_yl[j+py-1] * E3_y[abs(j)];
         for (long k = -pz+1; k <= pz; k++){
           Vz = Vy * E2_zl[k+pz-1] * E3_z[abs(k)];
-          ig = (ip+i+nx) % nx; jg = (jp+j+ny) % ny; kg = (kp+k+nz) % nz;
+          ig = (ip+i+nx*px) % nx; jg = (jp+j+ny*py) % ny; kg = (kp+k+nz*pz) % nz;
           for (long m = 0; m < DIM; m++){
             vel[DIM*n+m] += scale_factor * Vz * H[kg + ny*(jg + nz*(ig + m*nx))];
             vel_part[DIM*n+m] += scale_factor * Vz * H[kg + ny*(jg + nz*(ig + m*nx))];
[…]

### 2019-05-28 src/ewald.cu

@@ -268,7 +268,7 @@ void Gaussian_Gridding_type1_OMP(double *H){
       E2_zl[k+pz-1] = pow(E2_z, k);
     }
     V0 = E1_x * E1_y * E1_z;
-    #pragma omp parallel for schedule(dynamic, 1) private(Vx, Vy, Vz, ig, jg, kg)
+    #pragma omp parallel for private(Vx, Vy, Vz, ig, jg, kg)
     for (long i = - px+1; i <= px; i++){
       // printf("i=%d, from thread = %d\n", i, omp_get_thread_num());
       Vx = V0 * E2_xl[i+px-1] * E3_x[abs(i)];
@@ -276,7 +276,7 @@ void Gaussian_Gridding_type1_OMP(double *H){
         Vy = Vx * E2_yl[j+py-1] * E3_y[abs(j)];
         for (long k = -pz+1; k <= pz; k++){
           Vz = Vy * E2_zl[k+pz-1] * E3_z[abs(k)];
-          ig = (ip+i+nx) % nx; jg = (jp+j+ny) % ny; kg = (kp+k+nz) % nz;
+          ig = (ip+i+nx*px) % nx; jg = (jp+j+ny*py) % ny; kg = (kp+k+nz*pz) % nz;
           for (long m = 0; m < DIM; m++){
             H[kg + nz*(jg + ny*(ig + m*nx))] += Vz * strength[DIM*n+m];
           }
@@ -345,7 +345,7 @@ void Gaussian_Gridding_type1(double *H){
         Vy = Vx * E2_yl[j+py-1] * E3_y[abs(j)];
         for (long k = -pz+1; k <= pz; k++){
           Vz = Vy * E2_zl[k+pz-1] * E3_z[abs(k)];
-          ig = (ip+i+nx) % nx; jg = (jp+j+ny) % ny; kg = (kp+k+nz) % nz;
+          ig = (ip+i+nx*px) % nx; jg = (jp+j+ny*py) % ny; kg = (kp+k+nz*pz) % nz;
           for (long m = 0; m < DIM; m++){
             H[kg + nz*(jg + ny*(ig + m*nx))] += Vz * strength[DIM*n+m];
           }
@@ -414,7 +414,7 @@ void Gaussian_Gridding_type2_OMP(double* H){
[…]

### 2019-05-28 src/conv/ewald.cu
fix some bugs of conv

@@ -461,6 +461,7 @@ void Gaussian_Gridding_type2(double* H){
   double* E2_xl = (double*) calloc(2*px, sizeof(double));
   double* E2_yl = (double*) calloc(2*py, sizeof(double));
   double* E2_zl = (double*) calloc(2*pz, sizeof(double));
+  double* vel_part = (double*) calloc(np*DIM, sizeof(double));
   double V0, Vx, Vy, Vz;
   for (long i = 0; i <= px; i++) {
     E3_x[i] = exp(-a*i*i*hx_sq);
@@ -502,6 +503,7 @@ void Gaussian_Gridding_type2(double* H){
           ig = (ip+i+nx*px) % nx; jg = (jp+j+ny*py) % ny; kg = (kp+k+nz*pz) % nz;
           for (long m = 0; m < DIM; m++){
             vel[DIM*n+m] += scale_factor * Vz * H[kg + ny*(jg + nz*(ig + m*nx))];
+            vel_part[DIM*n+m] += scale_factor * Vz * H[kg + ny*(jg + nz*(ig + m*nx))];
           }
         }
       }
@@ -510,6 +512,9 @@ void Gaussian_Gridding_type2(double* H){
   printf("Gaussian_Gridding_type2 finished with %f(s)\n",(omp_get_wtime()-tt));
   free(E3_x);free(E3_y);free(E3_z);
   free(E2_xl);free(E2_yl);free(E2_zl);
+  string outputfilepart = "../../results/kspace.txt";
+  writeoutpart(vel_part,outputfilepart);
+  free(vel_part);
   return;
 }
 

### 2019-05-28 src/matlab/main.m

@@ -61,7 +61,7 @@ for i=1:length(pr_all)
     pr=pr_all(i);
     for j=1:length(xi_all)
         xi=xi_all(j);
-        eta=(P*L/M*xi/m);
+        eta=(P*L/M*xi/m)^2;
         status = system(['./main ',num2str(numthreads),' ',num2str(M),' ',num2str(np),' ',num2str(P/2),' ',num2str(pr),' ',...
             num2str(L),' ',num2str(xi),' ',num2str(eta)],'-echo');
         if status~=0
@@ -80,9 +80,10 @@ for j=1:length(xi_all)
     for i=1:length(pr_all)-1
         data1=vel_rec{i,j};
         err=sqrt(sum((data1-data0).^2,2));
-        error(i,j)=norm(err,2)/sqrt(sum(sum(data0.^2,2)));
+%         error(i,j)=norm(err,2)/sqrt(sum(sum(data0.^2,2)));
+        error(i,j)=mean(err)/np/sqrt(3);
         %     data0=data1;
-    end
+    end 
 end
 err_bound=@(pr,xi)(12*pi/xi^2+16*sqrt(pi)*pr/xi).*exp(-pr.^2.*xi^2);
 figure;
@@ -103,12 +104,12 @@ addpath ../matlab/
 DIM=3;
 L = 1;
 % M = 8; %nx
-M_all=[16,32,64];
+M_all=linspace(24,64,5);
 % M_all=20;
 % xi = 1;
-xi_all=[15,20,25];
-m = 8; %std of sigma of gaussian kernel
-P = 20; %points within support of Gaussian kernel
+xi_all=[5,10,15]; 
+m = 20; %std of sigma of gaussian kernel
+P = 64; %points within support of Gaussian kernel
 pr = 1; % layers of real space
 np = 100; % # of points
 numthreads = 4;
@@ -122,9 +123,10 @@ for i=1:length(M_all)
     M=M_all(i);
     for j=1:length(xi_all)
         xi=xi_all(j);
-        eta=(P*L/M*xi/m);
+        P=M;
+        eta=(P*L/M*xi/m)^2;
         status = system(['./main ',num2str(numthreads),' ',num2str(M),' ',num2str(np),' ',num2str(P/2),' ',num2str(pr),' ',...
-            num2str(L),' ',num2str(xi),' ',num2str(eta)],'-echo');
[…]

### 2019-05-28 src/matlab/main.m
finalize report

@@ -93,7 +93,7 @@ for j=1:length(xi_all)
     plot(pr_all(1:end-1),error,'color',[0 0.4470 0.7410]);
     plot(pr_all(1:end-1),err_bound(pr_all(1:end-1),xi),'--','color',[0.8500 0.3250 0.0980]);
 end
-ylabel('Relative Error of real space')
+ylabel('Error of real space')
 set(gca,'YScale','log','YLim',[1.0e-15,1.0e2],'FontSize',14)
 
 %%
@@ -156,5 +156,5 @@ for j=1:length(xi_all)
     plot(M_all(1:end-1),error,'color',[0 0.4470 0.7410]);
     plot(M_all(1:end-1),err_bound(M_all(1:end-1),M_all(1:end-1),xi),'--','color',[0.8500 0.3250 0.0980]);
 end
-ylabel('Relative Truncation Error of k-space')
+ylabel('Error of k-space')
 set(gca,'YScale','log','FontSize',14)
